\chapter{Control problems with $L^q$ penalizations, $q\in[0,1)$}\label{chap3}

	
		\section{Introduction}
		Optimal control problems with nonconvex $L^q$-quasinorm penalizations, with $q\in[0,1)$, can be regarded 
		as an extension of $L^1$-penalized control problems, whose main feature is the promotion of 
		sparsity in the optimal control. In this setting, the objective is to enforce a higher degree 
		of sparsity than the one induced by the $L^1$ penalization. To illustrate this idea, 
		let $\Omega\subset\mathbb{R}^n$, $n=2,3$, be an open domain with Lipschitz boundary, 
		and for $u\in L^2(\Omega)$ define
		\[
		\jzero{u}:=\int_{\om} \chi_{\{x\in\om: u(x)\ne 0\}}\; dx
		\]
		Then, clearly $\jzero{u}$ measure the volume of the set $\{x\in\om: u(x)\ne 0\}$. So, if this term
		is added as a penalizer over a cost function, the optimal control must satisfy a minimum support's
		volume criterion. However, the term $\jzero{u}$ is nor convex nor differentiable, even nor continuous. Thus, the control problem penalized with 
		such a penalizer cannot be analyzed with standar tools of theory of optimal control problems or
		convex analysis. Evenmore, in general, problems penalized with the $\jzero{\cdot}$ term might not
		have a solution. Problems with the term $\jzero{\cdot}$ are called $L^0$ penalized problems.
		
		In this context, $L^q$ penalizers arise as a sort of regularization of the so called $L^0$ sparse 
		problems.  However, depending on the regulization parameters present in the cost function, optimal controls
		induced by the  $L^q$-quasinorm entail subtle jump discontinuities and sparse properties that differs from 
		those optimal controls generated by the $L^0$-pseudo norm; for instance, $L^q$ optimal controls may have 
		smaller supports and, moreover, jump discontinuities may be not monotone. These properties 
		are relevant for optimal control as they enhance the sparsity and jump discontinuities 
		characterization of the optimal controls. Moreover, jump discontinuities in $L^q$ penalized problems appear at 
		the boundary of optimal control's support. This feature is potentially advantageous in several 
		applications. 	In particular, the sparsification effect induced by these penalizers are useful in
	 	applications requiring a sharp localized action of the control within the domain, which is crucial 
	 	for instance, to reduce the cost of the tracking term, see \cite{casas}.  Other examples arising 
	 	from inverse 	sparse reconstruction problems and image-processing-related applications can 
	 	benefit from solutions with jump discontinuities. For instance, in imaging, the so called 
	 	$TV^q$ penalizer enforces certain graphical features. 

		This chapter is devoted to the study of the existence of solutions for optimal control problems with $L^q$ 
		penalizations, $q\in[0,1)$, as well as to the derivation of optimality systems based on first-order necessary 
		conditions. These results are essential for the convergence analysis of the semismooth Newton (SSN) method applied to 
		the numerical treatment of the problems introduced in this chapter (see Chapter~4), and they also constitute a fundamental 
		basis for the error analysis associated with finite element method (FEM) discretizations, which will be addressed in 
		Chapter~5.
		
		We formulate the optimal control problem that we study throughout this work.
		 Let $q\in [0,1)$. For a measurable function $u: \om \to \reals$, 
		 we define the $L^q$ regularizer as
		\begin{equation}\label{eq:l_q}
			\jq{u}:=\begin{cases}
				\int_{\om} |u(x)|^q \; dx,& q>0,\\
				\mbox{meas }\{x\in \om: u(x)\ne 0\}&q=0.
			\end{cases}
		\end{equation}
		Notice that, if we define the function $|\cdot|_{0}:\mathbb{R}\to\mathbb{R}$ by
		\begin{equation}\label{eq:indicator}
		|t|_{0} =
		\begin{cases}
		0, & \text{if } t = 0,\\
		1, & \text{otherwise},
		\end{cases}		
		\end{equation}

		then	
		\begin{equation}\label{eq:l_0}
			\jzero{u}:=\int_{\om} |u(x)|_{0} \; dx,
		\end{equation}
				
		By definition, it is clear that, for any $q\in[0,1)$, the term $\jq{\cdot}$ is nonconvex. 
		In the case $q>0$, the functional $\jq{\cdot}$ is continuous but not differentiable, 
		whereas for $q=0$ it is not even continuous. The nonconvexity of $\jq{\cdot}$ entails the loss of weak 
		lower semicontinuity when compared with continuous and convex penalizations. Consequently, the combined lack of 
		differentiability and weak lower semicontinuity implies that the existence of solutions for optimal control problems 
		penalized by such terms cannot be inferred using standard tools from convex analysis.

		\subsection{$L^q(\om)$ spaces, $q\in (0,1)$}
		In this subsection we explore some properties of the $L^q(\om)$ spaces; particularly
		we study the strucutre that penalizers of the form \eqref{eq:l_q} induces over the 
		space of absolute Lebesgue integrable functions. From the definition of \eqref{eq:l_q},
		it is clear that such structure does not induce a normed space. However, there exists
		some topological and geometrical properties induced by this term. For a more extended 
		study of these kind of spaces, see for example \cite[Chapter 25]{geometry_banach_spaces}.
		\begin{definition}		
		Let $X$ a real or complex vector space. A funtion $\norm{\cdot}_{*}:X\to [0,+\infty)$ is said 
		to be a a quasi-norm on $X$ if
		\begin{enumerate}
			\item $\norm{x}_{*}=0$ if and only if $x=0$,
			\item $\norm{\alpha x}_{*}=|\alpha|\norm{x}_{*}$ for any $x\in X, \alpha>0$,
			\item There exists a constant $c\ge 1$ such that $\norm{x+y}_{*}\le c(\norm{x}_{*}+\norm{y}_{*})$ for any $x,y\in X$.
		\end{enumerate}
		The space $(X, \norm{\cdot}_{*})$ is called a quasi--normed space.
		\end{definition}
		\begin{definition}
		The quasi-norm $\norm{\cdot}_{*}$ is said to be $q$--subadditive is $\norm{x+y}_{*}^{q}\le \norm{x}_{*}^q+\norm{y}_{*}^q$ 
		for any $x,y\in X$ and $q\in (0,1]$.
		\end{definition}

		\begin{definition}
		Let $(X, \norm{\cdot}_{*})$ be a quasi--normed space, $q\in (0,1)$. If there exists a constant $B>0$ such that for any finite colection
		$\{x_1,\cdots,x_n\}\subset X$,
		\[
		\l\|\sum_{i=1}^n x_i\r\|_{*}\le B\l(\sum_{i=1}^{n}\norm{x_i}_{*}^q\r)^{1/q},
		\]
		then, $X$ is called $q$--normable. 
		\end{definition}

		\begin{definition}
		If $\norm{\cdot}_{*}$ is a quasi-
		norm and $q$--subadditive, then the space $X$ is called
		a quasi--Banach space if $(X, d_q)$ is a complete metric space, where
		\[
		d_q(x,y):=\norm{x-y}_{*}^q.
		\]
		\end{definition}
		
		The following property, known as the Aoki-Rolewicz Theorem, establish that  if 
		$X$ is a quasi--normed space with $C=2^{\frac{1}{q}-1}$ and $q\in (0,1]$, then $X$ is a 
		$q$--normable space, see \cite[Chapter 25]{geometry_banach_spaces}.

		We define the $L^q(\om)$ spaces, $q\in (0,1)$ as
		\[
		L^q(\om):=\l\{u\in L^1(\om): \int_{\om} |u(x)|^q \; dx<+\infty\r\}.
		\]
		The function $\norm{\cdot}_{L^q(\om)}:L^1(\om)\to \mathbb{R}$ defined by 
		$\norm{u}_{L^q(\om)}:=\l(\int_{\om} |u(x)|^q \; dx\r)^{\frac{1}{q}}$ is a quasi-norm on $L^q(\om)$.
		which is also $q$--subadditive. Moreover, $L^q(\om)$ is $q$--normable. To see these facts,
		first we prove a short result about a useful property of the function $|\cdot|^q$.
		\begin{proposition}\label{prop:prop1}
			For any $a,b\in [0,\infty)$, we have that $(a+b)^q\le a^q+b^q$.
		\end{proposition}
		\begin{proof}
			If $a=0$ or $b=0$, the equality holds trivialy, so asume that $a,b>0$.
			By the generalized reverse Bernoulli inequality \cite[Lemma 2.4]{li_yeh_bernoulli_2013}, 
			and without loss of generality, assuming that $a\le b$,
			\begin{align*}
				\l(1+\frac{a}{b}\r)^q&\le 1+q\l(\frac{a}{b}\r)\\
				&\le 1+q\l(\frac{a}{b}\r)\l(\frac{a}{b}\r)^{q-1}\\
				&\le 1+\l(\frac{a}{b}\r)^{q},
			\end{align*}
			since $0<q<1$. Multiplying both sides of he last inequiality by $b^q$, 
			we obtain the desired result.
		\end{proof}

		By Proposition \ref{prop:prop1} and the monotonicity of the function $t\mapsto t^q$ for 
$0<q\le1$ and $t\ge 0$, we have that for any $u,v\in L^{q}(\om)$,
\begin{equation}\label{eq:q_subadditivity}
\begin{aligned}
\norm{u+v}_{L^q(\om)}^q
&= \int_{\om}|u(x)+v(x)|^q\, dx \\
&\le \int_{\om}\big(|u(x)| + |v(x)|\big)^{q}\, dx \\
&\le \int_{\om}|u(x)|^q\, dx
+ \int_{\om}|v(x)|^q\, dx \\
&= \norm{u}_{L^q(\om)}^q
+ \norm{v}_{L^q(\om)}^q .
\end{aligned}
\end{equation}

Finally, by the convexity of the function $t\mapsto t^{\frac{1}{q}}$ for any $t$,
\begin{equation}\label{eq:1/q_convexity}
\begin{aligned}
\l(\norm{u}_{L^q(\om)}^q + \norm{v}_{L^q(\om)}^q\r)^{\frac{1}{q}}
&= 2^{\frac{1}{q}}
\l(\frac{\norm{u}_{L^q(\om)}^q+ \norm{v}_{L^q(\om)}^q}{2}\r)^{\frac{1}{q}}\\
&\le 2^{\frac{1}{q}}
\frac{\norm{u}_{L^q(\om)}+ \norm{v}_{L^q(\om)}}{2}\\
&= 2^{\frac{1}{q}-1}
\l(\norm{u}_{L^q(\om)}+ \norm{v}_{L^q(\om)}\r).
\end{aligned}
\end{equation}
Thus, combining \eqref{eq:q_subadditivity} and \eqref{eq:1/q_convexity}, we have that
$L^q(\om)$ satisfies the third property of a quasi--norm. The other two properties
follows from well known properties of the Lebesgue integral. Moreover,
since the constant $c$ that satisfies the third property of a quasi--norm
is $c=2^{\frac{1}{q}-1}$, we have that $L^q(\om)$ is $q$--normable acording to
Aoki-Rolewicz Theorem. Thus, the following Lemma follows.
\begin{lemma}
	The space $(L^q(\om),\norm{\cdot}_{L^q(\om)})$, where $0<q<1$ is a quasi--normed space. Moreover, it is $q$--normable.
\end{lemma}


	\begin{figure}[H]
\centering
\begin{tikzpicture}
\begin{axis}[
    axis equal,
    width=0.55\textwidth,
    height=0.55\textwidth,
    xmin=-1.2, xmax=1.2,
    ymin=-1.2, ymax=1.2,
    samples=400,
    domain=0:360,
    xlabel={$x$},
    ylabel={$y$},
    legend style={
        at={(0.97,0.97)},
        anchor=north east,
        draw=black,
        fill=white,
        font=\small
    }
]
% q = 0.3
\addplot [blue, thick, parametric]
({sign(cos(x))*abs(cos(x))^(2/0.3)},
 {sign(sin(x))*abs(sin(x))^(2/0.3)});

% q = 0.5
\addplot [red, thick, parametric]
({sign(cos(x))*abs(cos(x))^(2/0.5)},
 {sign(sin(x))*abs(sin(x))^(2/0.5)});

% q = 0.8
\addplot [green!60!black, thick, parametric]
({sign(cos(x))*abs(cos(x))^(2/0.8)},
 {sign(sin(x))*abs(sin(x))^(2/0.8)});

\legend{$q=0.3$, $q=0.5$, $q=0.8$}

\end{axis}
\end{tikzpicture}
\caption{Graphical representation of the sets $B_q:=\{(x,y)\in\mathbb{R}^2: |x|^q+|y|^q=1\}$ for different 
values of $q$. The difference between these sets and the unitary spheres in $\mathbb{R}^2$ are
quite evident, specially by the lack of convexity of the sets $B_q$.}
\label{fig:lq_balls}
\end{figure}


\begin{remark}
	The $L^q(\om)$ is a quasi--Banach space. Moreover, the standard basic results of Banach space theory such as the 
	Uniform Boundedness Principle, Open Mapping Theorem and Closed Graph 
	Theorem which depend only on completeness apply to this type of space; 
	however applications of convexity such as the Hahn-Banach theorem are not applicable, see \cite[Chapter 25]{geometry_banach_spaces}.
\end{remark}

\begin{proposition}\label{prop:continuity_lq}
The functional $\jq{\cdot}$ defined by $\jq{u}=\norm{u}_{L^q(\om)}^q$ defines a continuous 
Nemitski operator from $L^p(\om)$ to $L^p(\om)$ for any $p\ge 1$.
\end{proposition}

\begin{proof}
	Consider the function $t\mapsto |t|^q-|t|$ for $0<q<1$. This function is differentiable
	in all $\mathbb{R}\setminus \{0\}$. An easy computation shows that $|t_q|:=q^{\frac{1}{1-q}}$
	are the two global maximums of this function, so
	\[
	|t|^q-|t|\le q^{\frac{q}{1-q}}-q^{\frac{1}{1-q}},
	\]
	and since $0<q<1$, we have that 
	$$q^{\frac{q}{1-q}}-q^{\frac{1}{1-q}}=q^{-1+\frac{1}{1-q}}-q^{\frac{1}{1-q}}=q^{\frac{1}{1-q}}\l(\frac{1}{q}-1\r)>0.$$
	Therefore, we see that 
	$$ |t|^q\le \l( q^{\frac{q}{1-q}}-q^{\frac{1}{1-q}}\r)+|t|,$$
	so Theorem \ref{thm:nemitski} applies, and the conclusion follows.
\end{proof}

By Proposition \ref{prop:continuity_lq}, $\jq{\cdot}$
is continuous from $L^2(\om)$ to $L^2(\om)$. However, its lack of convexity makes
that this one is not a weakly lower semicontinuous function.

\subsection{The $L^0(\om)$ space}\label{subsec:l0_space}

We define the space $L^0(\om)$ as the set of measurable functions with domain
$\om$, endowed with the so called Eckeland distance
\begin{equation}\label{eq:Eckeland}
	d_0(f,g)=\text{meas}\{x\in\om: f(x)\neq g(x)\}, \quad \text{ for all }f, g\in L^0(\om).
\end{equation}
With this metric, the space is a metric complete space, see \cite{ito-kunisch2014}. 
Moreover, it is clear that $\jzero{f}=d_0(f,0)$ for all $f\in L^0(\om)$.
However, the term $\jzero{f}$ is not even a quasi--norm. In fact,
it is not homogeneous, because for any measurable function $f$ with a support with positive measure,
$\lambda f$ still have a support with positive measure for any $|\lambda|>0$. Thus 
$\jzero{\lambda f}=\jzero{\cdot}$. However, if $|\lambda|\ne 1$, then
$|\lambda|\jzero{\cdot}\ne \jzero{\cdot}$. However, since $\jzero{\cdot}$
comes from the metric $d_0$, the positivity and the triangular inequality hold. For these
reasons, we call the term $\jzero{\cdot}$ as a \textit{pseudonorm}. In addition,
due to the lack of homogenity of this term, it is not convex, because for any 
$0<\lambda<1$, we have 
\[
\jzero{\lambda f+(1-\lambda)0}=\jzero{\lambda f}=\jzero{f}
\]
so, if we need that $\jzero{f}\le \lambda \jzero{f}$, it is 
necessary that $\lambda\ge 1$, which is impossible since we assume $\lambda<1$. 

In addition, the funtion $\jzero{\cdot}$ is not 
continuous from $L^p(\om)$ to $L^p(\om)$. Indeed, for $\om=(0,1)$ and taking
the Lebesgue measure, define $f_n(x):=n^{-\frac{1}{p}}$. Therefore, 
\[
\int_{0}^{1}|f_n(x)|^p\; dx = \int_{0}^{1}|n^{-1/p}|^p=n^{-1},
\]
thus $\jzero{f_n}=n^{-1/p}\to 0$ as $n\to \infty$. On the other hand, since 
$f_n(x)\ne 0$ for any $x\in (0,1)$, we have that $\jzero{f_n}=1$.
for all $n\in \mathbb{N}$. However, $\jzero{f_n}=0$. Thus, 
$f_n\to 0$ but $1=\jzero{f_n}_{L^0(0,1)}\nrightarrow 0=\jzero{0}$.

However, the term $\jzero{\cdot}$ is weakly lower semicontinuous.The 
following result shows this fact.

\begin{proposition}
	Let $\om$ a set with finite measure. Then, the function 
	$\jzero{\cdot}$ is lower semicontinous in $L^p(\om)$ for any $p\ge 1$,
	i.e., if $(f_n)_{n\in\mathbb{N}}$ is a strong convergent 
	sequence in $L^p(\om)$ which converges to some $f$ in $L^p(\om)$, then
	then
	\[
	\jzero{f}\le \liminf_{n\to\infty} \jzero{f_n}.
	\]
\end{proposition}
\begin{proof}
	Recall that
	\[
	\jzero{f}=\text{meas}\{x\in \om: f(x)\neq 0\}, \quad \jzero{f_n}=\text{meas}\{x\in \om: f_n(x)\neq 0\}.
	\]
	Take $l=\liminf_{n\to\infty}\text{meas}\{x\in \om: f_n(x)\neq 0\}$. Then, by definition there exists
	a subsequence $(f_{n_k})_{k\in\mathbb{N}}\subset (f_{n})$ such that
	\[
	\text{meas}\{x\in \om: f_{n_k}(x)\neq 0\}\to l.
	\]
	But, $f_{n_k}\to f$ in $L^p(\om)$. Therefore, by classical results about 
	$L^p(\om)$ spaces, see for instance \cite[Theorem 2.3]{ambrosetti}, we
	hae the existence of a subsequence of $(f_{n_k})_{k\in\mathbb{N}}$ without renaming for avoiding 
	too many notations, such that $f_{n_{k}}(x)\to f(x)$ almost all $x\in \om$ as $k\to\infty$.
	Clearly, for any $x\in \om$, we have 
	\[
	\chi_{x\in \om:\{f(x)\neq 0\}}(x)\le \liminf_{k\to\infty} \chi_{\{x\in \om:f_{n_k}(x)\neq 0\}}(x), 
	\]
	because if $x$ is such that $f(x)=0$, then  $\chi_{x\in \om:\{f(x)\neq 0\}}(x)=0$, and
	since $\chi_{x\in \om: \{f_{n_k}(x)\neq 0\}}(x)\in \{0,1\}$ for all $x$ and all $k$, the claim follows. On the
	other hand, if	$x$ is such that $f(x)\ne 0$, since $f_{n_k}(x)\to f(x)$, we must have that 
	for enough large $k$, $f_{n_k}(x)\ne 0$, thus $\chi_{x\in \om:\{f_{n_k}(x)\neq 0\}}(x)=1$. Therefore, 
	$\lim_{n\to \infty}\chi_{x\in \om:\{f_{n_k}(x)\neq 0\}}(x)=1$. By Fatou's Lemma:
	\begin{align*}
	\jzero{f}&=\int_{\om}\chi_{\{x\in \om:f(x)\neq 0\}}(x)\; dx \\
	&\le \int_{\om}\liminf_{k\to\infty} \chi_{\{x\in \om:f_{n_k}(x)\neq 0\}}(x)\; dx\\
	&\le \liminf_{k\to\infty} \int_{\om} \chi_{\{x\in \om:f_{n_k}(x)\neq 0\}}(x)\; dx\\
	&=\liminf_{k\to \infty} \text{meas}\{x\in \om: f_{n_k}(x)\neq 0\}\\
	&=l\\
	&=\liminf_{n\to\infty}\text{meas}\{x\in \om: f_n(x)\neq 0\}=\liminf_{n\to\infty}\jzero{f_n}.
	\end{align*}
\end{proof}

Despite the lower semicontinuity of $\jzero{\cdot}$, the weakly lower semicontinuity
of this over reflexive Banach spaces are missing by its lost of convexity. Therefore, the
application of the direct methods from variational analysis are not longer available. Evenmore
the existence of solution for these kind of problems is not guaranteed, see for example \cite{ito-kunisch2014}
for an extensive review of optimal control problems with $L^0$ regularizers.
		
		\subsection{Problem formulation}
		Let $\alpha, \beta>0$.For $q\in [0,1)$, define the cost function  $J: H_0^1(\om) \times L^2(\om) \to \reals$ as
	\begin{equation}\label{eq:cost_q}
		\displaystyle J{(y,u)}= ~\frac{1}{2}\| y-y_d \|^2_{L^2(\om)}+\frac{ \alpha}{2}\|u\|^2_{L^2(\om)}+\beta \jq{u}.
	\end{equation}

We formulate the following distributed optimal control problem using the objective functional \eqref{eq:cost_q} as follows:
	\begin{equation}
		\tag{$P$} \label{eq:OCP}
		\begin{cases}
			\displaystyle\min_{(y,u)} J(y,u)\\
			\hbox{ subject to: }\\
			\hspace{40pt}\begin{array}{rll}
				A y=&u + f, &\hbox{in  } \om, \\
				y=&0, &\hbox{on  }  \Gamma.
			\end{array}			
		\end{cases}
	\end{equation}
	In our setting, $\om \subset \reals^n$ is a bounded Lipschitz domain, and $y_d$ and $f$ are given functions in $L^2(\om)$.
	Moreover, $A$ is the differential operator defined as in \eqref{eq:operator_A} with $b_i\equiv 0$ for all $i$, i.e.,
	\begin{equation}\label{eq:A}
		(Ay) (x) = - \sum_{i,j=1}^n \frac{\partial}{\partial x_i}	\l( a_{ij}(x)\frac{\partial y(x)} {\partial x_j }\r) +c_0 y(x),
	\end{equation}
	%
	with coefficients $a_{ij}$ in $\rm{C}^{0,1}(\bar\om)$, and $c_0\geq 0$ in $L^{\infty}(\om)$. In addition, we assume that
	$A$ satisfies the coercivity property \eqref{eq:coercivity_A}.

	We recall the definition of the bilinear form $a(\cdot, \cdot):H_{0}^{1}(\om) \times H_{0}^{1}(\om)\to \reals$  
	defined in \eqref{eq:bilinear_form} with $b_i\equiv 0$:
	$$a(y,v)=\int_\om a_{ij}(x)\frac{\partial y(x)}{\partial x_i} \frac{\partial v(x)}{\partial x_i} dx + \int_\om c_0(x)\,y(x)v(x)\,dx, $$
	while $a^*$ denotes the corresponding bilinear operator associated to $A^*$.
	
	

As we discussed in \ref{subsection:regularity_pde_sol}, under the hypothesis of the domain as the
coefficients of $A$, we have have that if $y$ is a solution of \eqref{eq:variational_formulation}, then 
$y\in L^{\infty}(\om)$, and moreover the boundedness \eqref{eq:esti_state_uniform} follows. Similar results are valid for 
the solution $z$ of the adjoint problem \eqref{eq:variational_formulation*}, with the boundedness result 
\eqref{eq:esti_state*_uniform} following.  


	\section{Existence of solution and optimality conditions }
    
	We argue for the existence of a solution to problem \eqref{eq:OCP}, with $q\in (0,1)$,
	 following the methodology presented in \cite{ito-kunisch2014}, where the authors demonstrated the existence of a solution using the $L^0$-pseudonorm as a penalizer in the cost function. We proceed by first deriving the first-order necessary optimality conditions that characterize solutions to \eqref{eq:OCP}. Then, after obtaining a solution to these conditions, we will verify that it is, indeed, a global minimum for \eqref{eq:OCP}.
	
	The adjoint state is an essential tool to represent optimality conditions.
	 Given a control $u \in L^2(\om)$ with associated state $y\in H_{0}^{1}(\om)$, 
	 we introduce the adjoint state $\varphi$ as the solution of the following
	  variational problem, which can be in the same way as problem \eqref{eq:variational_formulation*}: 
	\begin{align}\label{eq:costate}
		&a^*(\varphi,v) = (y_d-y,v)_{L^2(\om)}, \quad \forall v \in H_{0}^{1}(\om)
	\end{align}	
	
	We define the Hamiltonian associated with the optimal control \eqref{eq:OCP} problem as follows:
	\begin{equation} \label{eq:Hamiltonian}
    \mathcal{H}(x,y,u,p):=\frac12 |y-y_d|^2+\frac{\alpha}{2}u^2 + \beta |u|^q + p u.
    \end{equation}
	
	We apply Theorem 2.2 in \cite{ito-kunisch2014} by choosing $\ell(x,y(x))=\frac{1}{2}(y(x)-y_d)^2$, $h(u)=\frac{\alpha}{2}|u|^2+\beta|u|^q$, $f(\cdot,y,u(\cdot))=u(\cdot)$, $\langle Ey,\cdot\rangle_{X^*,X}=a(y,\cdot)$ and $X=H_{0}^{1}(\om)$. This setting verifies the hypothesis of \cite[Theorem 2.2]{ito-kunisch2014}; therefore,  if $(\bar y, \bar u)$ is a solution of  \eqref{eq:OCP}, and $\varphi$ is the associated adjoint state, we conclude that for almost all $x \in \om$ it holds: 
	$$
		\mathcal{H}(x,\bar y(x),\bar u(x),\varphi (x))\leq \mathcal{H}(x,\bar y(x),u,\varphi (x)),
	$$
	 for all $u \in \reals$ and almost all $x\in\om$. 
	 
	 Writing the last relation explicitly we find that $\bar u(x)$ satisfies
	\begin{equation}\label{eq:fonc_H}
		\frac{\alpha}{2}\bar u(x)^2 + \beta |\bar u(x)|^q + \varphi(x) \bar u(x) \leq \frac{\alpha}{2}u^2 + \beta |u|^q + \varphi(x) u
	\end{equation}
	for almost all $x$ and all $u\in \reals$. 
	
	Taking into account \eqref{eq:fonc_H}, we seek to characterize $\bar u(x)$ for almost all $x\in \om$ by studying the following one-dimensional problem:
	\begin{equation}\label{eq:1dlq}
		\bar u \displaystyle\in  \argmin_{t\in \reals} \left\{g(t):= \frac{\alpha}{2}t^2+\beta |t|^q + pt \right\},
	\end{equation}
	where $p$ is a given real number.
	
	
	It is clear that if $\alpha>0$, then $g$ has at least one minimum, because it is continuous and coercive. 
	First, let us consider the case where a minimum $\bar u \not =0$. 
	Then, $g$ is differentiable and $\bar u$ satisfies the necessary condition 
	\begin{equation}\label{eq:1d_fonc}
		\alpha \bar u + \beta q |\bar u|^{q-1} \sign (\bar u) + p= 0. 	
	\end{equation}
	%
	Multiplying the last equality by $\bar u$ and replacing 
	$p\bar u=-\alpha\bar u^2-\beta q |\bar u|^{q}$ in $g(\bar u)$, 
	we have  that $\bar u$  satisfies the condition:	
	$$ 
	  0=g(0)\geq g(\bar u) = \frac{\alpha}{2}\bar u^2 + \beta |\bar u|^{q} + p\bar u =  -\frac{\alpha}{2}\bar u^2 + \beta (1-q) |\bar u|^{q}.
	$$ 
Therefore, we deduce that
	\begin{equation}\label{eq:jump_bound}
		|\bar u| \geq \jump_q:=\l(2(1-q) \frac{\beta}{\alpha} \r)^{\frac{1}{2-q}}.
	\end{equation}
Thus, $|\bar u|$ is bounded away from 0 whenever it is not null, and $\jump_q$ estimates the jump discontinuity. Figure \ref{fig:jump} depicts the behavior of $\jump_q$ as a function of $q$ for fixed $\alpha$ and $\beta$. Here, we observe that for certain ratios $\beta/\alpha$ the convergence to $\jump_0=\sqrt{\frac{2\beta}{\alpha}}$ (when $q\to 0$), corresponding to the jump value of the $L^0$-pseudo norm is not monotone, and can reach larger values than $\sqrt{\frac{2\beta}{\alpha}}$.

\begin{figure}[ht!]
	\begin{center}
\begin{tikzpicture}[scale=0.9]
\begin{axis}[
    %title={Plot of $(2(x-1) \cdot 0.1)^{\frac{1}{2-x}}$ for $x$ in $[0,1]$},
    xlabel={$q$},
    ylabel={$\jump_q$},
    xmin=0, xmax=1,
    ymin=0, ymax=5.5, % Adjust the y-axis limits as necessary
    grid=both,
    minor tick num=1,
    major grid style={lightgray,dashed},
    minor grid style={lightgray,dotted},
    samples=100, % Increase for a smoother plot
    no marks,
    tick label style={font=\tiny},
    axis lines=middle,
    xlabel style={at={(ticklabel* cs:1)},anchor=north west}, % Adjust label position
    ylabel style={at={(ticklabel* cs:1)},anchor=south west} % Adjust label position
    ]
\addplot[blue, thick, domain=0:1] {(2*(1-x)*8)^(1/(2-x))} node[pos=0.3, above] {$\frac{\beta}{\alpha}=8$};
\addplot[orange, thick, domain=0:1] {(2*(1-x)*2)^(1/(2-x))} node[pos=0.25, above] {$\frac{\beta}{\alpha}=2$};
\addplot[red, thick, domain=0:1] {(2*(1-x)*12)^(1/(2-x))}node[pos=0.20, above] {$\frac{\beta}{\alpha}=12$};
\end{axis}
\end{tikzpicture}
\caption{Plot of the jump estimate  $\jump_q$ for different ratios $\beta/\alpha$. $\jump_0= \sqrt{2\beta/\alpha}$ at $q=0$ corresponds to $L^0$-pseudo norm penalizer.}	
\label{fig:jump}
\end{center}
\end{figure}
	

\begin{lemma}\label{l:thresholds} Let $\bar u \not =0$ be a minimizer of $g$, i.e. $\bar u$ satisfies \eqref{eq:1dlq}. Then, it follows that
$$|\bar u| \geq \jump_q, \quad \text{if and only if, }\quad |p|\geq \omega_q ,$$
where $\omega_q=\l( 2(1-q) \alpha^{1-q}\beta \r)^{\frac{1}{2-q}} + \beta q \l(2(1-q) \frac{\beta}{\alpha} \r)^{\frac{q-1}{2-q}}=\alpha\jump_q+\beta q\jump_q^{q-1}$.
\end{lemma}
\begin{proof}
Without loss of generality, let us suppose that $\bar u >0$. The case $\bar u <0$ follows by 
symmetric arguments. Now, since $t\mapsto t^{q-2}$ is nonincreasing for $t>0$,   
$$
t>\jump_q/(2^{1/(2-q)})\Rightarrow  \alpha -\beta q(1-q)  t^{q-2} > \alpha - \beta q(1-q)  \l(\frac{\jump_q}{2^{1/(2-q)}}\r)^{q-2} = \alpha - q\alpha >0,
$$
Thus, the function $t \mapsto \alpha t + \beta q t^{q-1}$ is strictly increasing for $t\geq\jump_q/(2^{1/(2-q)})$. 
Since $\bar u \geq \jump_q>\jump_q/(2^{1/(2-q)})$, and since $g'(\bar u)=0$,we have
	\begin{align}
		p = -\alpha \bar u - \beta q \bar u^{q-1}\leq & -\alpha \jump_q - \beta q  \jump_q^{q-1} \nonumber\\
		&=-\l( 2(1-q) \alpha^{1-q}\beta \r)^{\frac{1}{2-q}} - \beta q \l(2(1-q) \frac{\beta}{\alpha} \r)^{\frac{q-1}{2-q}}=-\omega_q,  \nonumber
	\end{align}
	%
 and conversely, if $p\leq -w_q$, then the strictly monotonicity of $t \mapsto \alpha t + \beta q t^{q-1}$  implies that $\bar u\geq\jump_q$.
\end{proof}

 The threshold quantity $\omega_q$ can be used to characterize a global solution of \eqref{eq:1dlq} in terms of the size of  $p$. Indeed, we define $\bar u = \Phi_q(p)$ given by
	
	\begin{equation}\label{eq:PHI1}
		%
		\Phi_q (p) =	
		%
		\begin{cases}
			\argmin_{u} g(u), & \text{ if } |p| > \omega_q, \\
			0,                          &	 \text{ otherwise.}
		\end{cases}
	\end{equation}
		%
	\begin{remark}\label{rmrk:exact_threshold}
	Equation \eqref{eq:PHI1} is semi-implicitly defined and, in practice, it has to be solved approximately. However, for the special cases $q=\frac12$ and $q=\frac23$, explicit solutions can be derived from the proximal mapping discussed in \cite{CaoZungXu2013}. Indeed, calculating the proximal of $|\cdot|^q$ we get:
	$$\text{\textnormal{prox}}_{|\cdot|^q,\frac{1}{\rho}}(t):=\argmin_{u} \l\{|u|^q+\frac{1}{2\rho}|u-t|^2 \r \},$$
that is equivalent to minimize $g$ defined in \eqref{eq:1dlq} for $\rho=\frac{2\beta}{\alpha}$. Thus, for $q=\frac12$, we have that $\varPhi_{\frac12}$ becomes:
		\begin{equation}\label{eq:PHI1 q=1/2}
		%
		\Phi_{\frac12} (p) =	
		%
		\begin{cases}
			\phantom{-}\frac23 |p|\big(1+\cos(\frac{2\pi-2 p_{\beta/\alpha} }{3})) \big), & \text{ if } p > \frac{54^{\frac13}}{4}\big(\frac{2\beta}{\alpha}\big)^{\frac23}, \\
			-\frac23 |p|\big(1+\cos(\frac{2\pi-2p_{\beta/\alpha}}{3})) \big), & \text{ if } p< -\frac{54^{\frac13}}{4}\big(\frac{2\beta}{\alpha}\big)^{\frac23}, \\
			\phantom{-}0,                          &	\text{ otherwise},
		\end{cases}
	\end{equation}
	with $p_{\beta/\alpha}=\arccos \Big(\frac{\beta}{4\alpha}\big(\frac{|p|}{3}\big)^{-\frac23}\Big)$.
\end{remark}	

	\begin{theorem}\label{t:monotone_phi}
		Given $p \in \reals$, $\Phi(p)$ is well defined, and $\bar u =\Phi(p)$ is a global solution for one-dimensional problem \eqref{eq:1dlq}.
	\end{theorem}
	
	\begin{proof}
		First, we consider the case $|p| \leq  \omega_q$. If $p=0$ is clear that $\bar u=0$ is a global solution for \eqref{eq:1dlq}. Let us prove that $\bar u =0$ is a global solution for \eqref{eq:1dlq} when $0<|p|\leq \omega_q$. Arguing by contradiction, suppose that $0 = \Phi(p)$ is not a global solution. Then, there is at least one point where the value of $g$ is below 0. By continuity and coercitivity of $g$, it reaches its minimum (without loss of generality) at some $\tilde u>0$ such that $g(\tilde u) <0$. Now, since $g$ is differentiable at $\tilde u$, it follows that 
		$$ 0 = g'(\tilde u) = \alpha \tilde u + \beta q (\tilde u)^{q-1} + p, $$		
		implying that  $$ 0 = g'(\tilde u)\tilde u = \alpha \tilde u^2 + \beta q (\tilde u)^{q} + p\tilde u = g(\tilde u) + \frac{\alpha}{2}\tilde u^2 + \beta (q-1) (\tilde u)^{q}. $$
		Considering that $g(\tilde u)<0$, we obtain that 
		$\beta (1-q) (\tilde u)^{q}<\frac{\alpha}{2}\tilde u^2$ which in turn implies 
		$\tilde u> \jump_q$. Thus, $p<-\omega_q$, accordingly to Lemma \ref{l:thresholds}, contradicting that $|p|\leq \omega_q$. The same arguments apply by assuming that $\tilde u<0$.
		
		On the other hand, if $|p|>\omega_q$, we shall prove that $\bar u = \Phi(p)$ is well defined by showing that in this case, $g$ has only one minimum.  Again, without loss of generality, we assume that $p<-\omega_q$. By symmetry, the arguments are analogous for $p>\omega_q$. Since $\bar u$ minimizes $g$, then $g(\bar u) \leq g(\jump_q)$. Replacing $\jump_q= (2(1-q)\frac{\beta}{\alpha})^{\frac{1}{2-q}}$, we obtain 
		%
		\begin{align*}
			g (\bar u) \leq   g(\jump_q) <& \frac{\alpha}{2} {\jump_q}^2 + \beta {\jump_q}^{q} -\omega_q \jump_q\\
			=&-\frac{\alpha}{2} {\jump_q}^2 + \beta(1-q) {\jump_q}^{q} = \jump_q^2\left(-\frac{\alpha}{2}+\beta (1-q)\jump_q^{q-2}\right)=0.
		\end{align*} 
		Therefore, $g(\bar u)\le g(\jump_q)<0$. Moreover, since 
		$p<-\omega_q$ implies that $g(u)\geq 0$ for all $u\leq 0$, then $\bar u>0$. 
		Furthermore, since $g$ is differentiable in $\reals^+$, then $\bar u$ must satisfy 
		
		\begin{equation}\label{eq:fonc_ell}
			\alpha \bar u + \beta q \bar u^{q-1} = -p .
		\end{equation}
		
		The function $s(u):= \alpha   u + \beta q   u^{q-1} $ defined for all $u>0$ 
		attains its minimum at $\hat u = \jump_q({q}/{2})^{\frac{1}{2-q}}$. In addition, 
		it is strictly increasing for all  $u> \hat u$ because its derivative
		is positive in this set. Therefore, since $p<-\omega_q$ if and only if $u>\jump_q>\hat{u}$ by 
		Lemma \ref{l:thresholds}, and moreover $p<-\omega_q$ implies that $-p>\omega_q=s(\jump_q)>s(\hat{u})$, the equation $s(u)=-p$ must have only one solution for any 
		$p<-\omega_q$, and, in particular, \eqref{eq:fonc_ell} has only one solution, which is, 
		in fact, a global solution for \eqref{eq:1dlq} because $g(\bar u)< g(u)$ for all $u\leq 0$, and $g(\bar u)\le g(u)$ 
		for all $u>0$.  
		
		Analogously, equation \eqref{eq:fonc_ell} has only one solution $\bar u<-\jump_q$, if $p>\omega_q$.
	\end{proof}
	%
\begin{figure}[ht!]
	\begin{center}
	\begin{tikzpicture}[scale=0.9]
	\begin{axis}[
    %title={Plot of $(2(x-1) \cdot 0.1)^{\frac{1}{2-x}}$ for $x$ in $[0,1]$},
    xlabel={$u$},
    ylabel={$\alpha u + \beta q u^{q-1}$},
    xmin=0.0, xmax=0.25,
    ymin=0.4, ymax=1.2, % Adjust the y-axis limits as necessary
    %grid=both,
    %minor tick num=1,
    %major grid style={lightgray},
    %minor grid style={lightgray!25},
    samples=250, % Increase for a smoother plot
    no marks,
    tick label style={font=\tiny},
    axis lines=middle,
    xtick={0.036, 0.1,0.142},
	xticklabels={$\hat u$,$\jump_q$,$\bar u$},
	ytick={0.612,0.75},
	yticklabels={$\omega(q)$,$-p$},%{-1,0,1},
    xlabel style={at={(ticklabel* cs:1)},anchor=north west}, % Adjust label position
    ylabel style={at={(ticklabel* cs:1)},anchor=south west} % Adjust label position
    ]
\addplot[blue, thick, domain=0:1] {4*x+ 0.06 9*(x+ 0.0051)^(-0.5)};

\end{axis}
\draw[dotted] (0.98,0) -- (0.98,0.6);
%
\draw[dotted] (2.739,0.0) -- (2.739,1.51);
\draw[dotted] (0.0,1.51) -- (2.739,1.51);
%
\draw[dashed, color=red, thick] (0,2.485) -- (3.9,2.485) node[anchor=north] {};
\draw[dashed, color=red, thick] (3.9,0) -- (3.9,2.49) node[anchor=north] {};
\draw[fill,color=red] (3.89,2.48) circle [radius=0.07];

\end{tikzpicture}	

		\caption{Solutions of the critical point equation \eqref{eq:fonc_ell} if $p<-\omega_q$}
		\label{fig:1}
	\end{center}
\end{figure}
	%-----------------------------------------------------------------------------------------
	
	From the analysis of the proof of Theorem \ref{t:monotone_phi} and the necessary condition \eqref{eq:1d_fonc}, we realize that this function is monotone increasing, and $\Phi_q$ can be written as follows:
	{%\color{blue}
		\begin{equation}\label{eq:Phi2}
			%
			\Phi_q (p) =	
			%
			\begin{cases}
				-\frac{p}{\alpha}-\frac{\beta}{\alpha} q |\bar u|^{q-1}\sign (\bar u), & \text{ if } |p|> \omega_q, \\
				0,                         &	\text{ otherwise.}
			\end{cases}
		\end{equation}
	}
	Although $\Phi_q$ is semi-implicitly defined because we need to know $\bar u$ in advance, we can observe that the limit case $q\to 0$  implies that $\omega_q \to \sqrt{2\alpha \beta}$
	\begin{equation*}
		%
		\Phi_q (p)  \to 	\Phi_0(p):=
		%
		\begin{cases}
			-\frac{p}{\alpha}, & \text{ if } |p|> \omega_q, \\
			0,                         &	\text{ otherwise,}
		\end{cases}
	\end{equation*}
	which is precisely the operator defined $L^2(\om)$ case studied in \cite{ito-kunisch2014} for the $L^0(\om)$ pseudonorm, when the set $\{x: |\varphi(x)|=0\}$ is of zero measure.
 
	Thanks to $\Phi_q$ and the adjoint equation \eqref{eq:costate}, we characterize the optimal control $\bar u$ together with associated optimal state $\bar y$ and adjoint state $\varphi$ as the solution of the following optimality system:
	\begin{subequations}\label{eq:system1}
		\begin{align} 
			&	\begin{array}{rll}
				A \bar y=& \bar u + f, &\hbox{in  } \om, \\
				\bar y=&0, &\hbox{on  }  \Gamma,
			\end{array} \\
			%	
			&\begin{array}{rll}
				A^*   \varphi=& \bar y -y_d, &\hbox{in  } \om, \\
				\varphi=&0, &\hbox{on  }  \Gamma, \label{eq:optimal_adjoint}
			\end{array}\\
			&\bar u (x) = \Phi_q (\varphi(x)), \quad  \text{a.a. } x \in \om, \label{eq:uPhi}
		\end{align} 	
	\end{subequations}
	%
	equivalently, $\bar u$, $\bar y$ and $\varphi$ satisfy
	\begin{subequations}\label{eq:system2}
		\begin{align} 
			&	\begin{array}{rll}
				A \bar y=& \bar u + f, &\hbox{in  } \om, \\
				\bar y=&0, &\hbox{on  }  \Gamma,
			\end{array} \\
			%	
			&\begin{array}{rll}
				A^*   \varphi=& \bar y -y_d, &\hbox{in  } \om, \\
				\varphi=&0, &\hbox{on  }  \Gamma,
			\end{array}\\
			&\alpha \bar u (x) + \beta q |\bar u(x)|^{q-1} \sign(\bar u(x)) + \varphi(x)  = 0, \quad a.a. \, x: |\varphi(x)|>\omega_q, \label{eq:system2_gradeq} \\
			& \bar u(x) =0, \quad a.a. \, x: \,  |\varphi(x)| \le \omega_q. \label{eq:null_control}
		\end{align} 	
	\end{subequations}
	
	
	Notice that by the definition of $\Phi_q$, $\bar u (x)$ defined in \eqref{eq:uPhi} fulfills the necessary condition \eqref{eq:fonc_H}. However, $\Phi_q$ is not a maximal monotone operator, hence system \eqref{eq:system1} might not have a solution.  To ensure the maximal monotonicity of $\Phi_q$, we extend $\Phi_q$ to a multifunction $\tilde \Phi_q:\reals \to 2^\reals$, defined by
	\begin{equation}\label{eq:Phi_ext}
		%
		\tilde\Phi_q (p)  =	
		%
		\begin{cases}
			-\frac{p}{\alpha}-\frac{\beta}{\alpha} q |\bar u|^{q-1}\sign (\bar u) & \text{ if } |p|>\omega_q, \\
			0,                          &	 \text{ if } |p|<\omega_q, \\
			[-\frac{\omega_q}{\alpha}+\frac{\beta}{\alpha} q |\jump_q|^{q-1}, 0] ,                         &	 \text{ if } p=\omega_q\\
			[0,\frac{\omega_q}{\alpha}-\frac{\beta}{\alpha} q |\jump_q|^{q-1}],                         &	 \text{ if } p=-\omega_q.
		\end{cases}
	\end{equation}
	
	
\begin{figure}
		\begin{center}
			\begin{tikzpicture}[scale=1]
			 %
				\begin{axis}[
					domain=-15 :15 ,
					samples=200,
					axis lines=middle,
					ymax=5,
					ymin=-5,
					xmax=3,
					xmin=-3,
					y post scale=-1.5,
					xtick={-2,-0.5,0,0.5,2},
					yticklabels={},%{-1,0,1},
					xticklabels={},%{-2,-0.5,0,0.5,2},
					axis line style={gray},
					anchor=origin, % Shift the axis so its origin is at (0,0)   
					rotate around={90:(current axis.origin)}, % Rotate around the origin
					]
					\addplot[color=blue, thick, domain=1.108:15 ] {1.2*x+0.7*abs(x)^(-0.5)};
					\addplot[color=blue, thick, domain=-15:-1.108 ] {1.2*x-0.7*abs(x)^(-0.5)};
					\addplot [thick,color=red,mark=.,mark size = 1pt,%fill=blue, 
					fill opacity=0.05]coordinates {
						(1.527, 1.833) 
						(0, 1.833)
						(0, -1.833)  
						(-1.527, -1.833)			}; 
					\addplot [thick,color=red,mark=.,mark size = 1pt,%fill=blue, 
					fill opacity=0.05]coordinates {
						% 
						(0, 1.833)
						(0, -1.833)  
								};    
					
					\addplot[color=red, thick, domain=1.527:15 ] {1.2*x};
					\addplot[color=red, thick, domain=-15:-1.527] {1.2*x};
					\addplot [thick,color=blue,mark=.,%fill=blue, 
					fill opacity=0.05]coordinates {
						(1.108, 1.994) 
						(0, 1.994)
						(0, -1.994)  
						(-1.108, -1.994)			};    
					\addplot [thick,color=blue,mark=.,%fill=blue, 
					fill opacity=0.05]coordinates {
						%  
						(0, 1.994)
						(0, -1.994) 	 
						 		};   
					 
					 \node [draw=black,anchor=center] at (axis cs: 2.4,-2.5) {
					 $
					 \begin{array}{l}
					  {\color{red} -\tilde\Phi_0}\\
					 %
					 {\color{blue} -\tilde\Phi_q, \quad \text{q=1/2}}\\
					 \end{array}
					 $
					 %
					 };
					 \node [anchor=center] at (axis cs: -0.3,4.5) {
					 $p$};
					 \node [anchor=center] at (axis cs: -0.3,2) {
					 $\omega_q$};
					 \node [anchor=center] at (axis cs: -0.3,-2.3) {
					 $-\omega_q$};
					 \node [anchor=center] at (axis cs: 2.4,0.5) {
					 $\bar u$};
				\end{axis}				
			\end{tikzpicture}
		\end{center}
		\caption{Ilustration of $-\tilde\Phi_q$ compared with the extension of the hard-thresholding operator.}
	\end{figure}

	Then, we consider the following generalized system 
	
	\begin{subequations}\label{eq:system2.5}
		\begin{align} 
			&	\begin{array}{rll}
				A   y - \tilde u \ni &f, &\hbox{in  } \om, \\
				y=&0, &\hbox{on  }  \Gamma,
			\end{array} \\
			%	
			&\begin{array}{rll}
				A^*   \varphi=& \bar y -y_d, &\hbox{in  } \om, \\
				\varphi=&0, &\hbox{on  }  \Gamma,
			\end{array}\label{eq:statey_2}\\
			&\tilde u (x) = \tilde\Phi_q (\varphi(x)), \quad  \text{a.a. } x \in \om. \label{eq:uPhi.1}
		\end{align} 	
	\end{subequations}
	
	%=====================================================================================
\begin{assumption}\label{as:phi_zero_measure}
    Suppose that $\bar u \in L^2(\om)$ is an optimal control for \eqref{eq:OCP} with 
	associated state $\bar y$ satisfying the state equation \eqref{eq:variational_formulation}
	 and $\varphi$ satisfying the adjoint equation \eqref{eq:variational_formulation*}. Then, the set
    $$\om_*=\{x \in \om : |\varphi(x)|=\omega_q\},$$
    is of measure zero.
\end{assumption}

\begin{remark}
    Assumption \ref{as:phi_zero_measure} is widely used in works related to $L^q(\Omega)$-type penalizations 
	with $q \in [0,1)$. In fact, in~\cite{ito-kunisch2014}, this assumption is imposed to ensure the existence 
	of solutions for problems with $q = 0$, where it is indicated that, if the assumption is not enforced, 
	the existence of solutions may fail to hold (see Remark 2.8). In more general contexts, Assumption \ref{as:phi_zero_measure} 
	is introduced to avoid issues related to the stability of bang-bang type solutions; see, for instance, 
	\cite{casas-wachsmuth-wachsmuth2017,deckelnick-hinze2010, corella-jork-veliov2022,wachsmuth2011}.
\end{remark}

The following Theorem contains the core of this subsection. Here, we prove two important results: the existence
of a solution for optimality system \eqref{eq:system2.5} and the exisntece of a solution for problem \eqref{eq:OCP}
 when Assumption \ref{as:phi_zero_measure} holds.
 \begin{theorem}\label{t:existence}
		Problem \eqref{eq:system2.5} admits a unique solution $(y,\varphi) \in H_{0}^{1}(\om) \times H_{0}^{1}(\om)$ with relaxed control $\tilde u = \tilde \Phi_q(\varphi)\subset L^2(\om)$. 
		If, in addition, Assumption \ref{as:phi_zero_measure} holds, then $\bar u = \Phi_q(\varphi)$ is the unique solution to problem \eqref{eq:OCP}.\end{theorem}
	\begin{proof}
		 The proof is analogous to the proof \cite[Section 2.2]{ito-kunisch2014}. However, we consider specifics aspects of the $L^q$ penalizer and $\Phi_q$ defined in \eqref{eq:Phi2}.  For the convenience of the reader, we write down the details. 
		
		As discussed earlier, condition \eqref{eq:1d_fonc} and the monotonicity of $\alpha u + \beta q |u|^{q-1}\sign(u)$ allowed us to define monotone the operator $-\Phi_q$ and its maximal monotone extension $-\tilde\Phi_q$  defined in \eqref{eq:Phi_ext}. This is the main tool for the proof.  
		
Notice that, from \eqref{eq:Phi_ext} and the fact that $u$ and $p$ have opposite signs when $|p|\geq \omega_q$, it holds that $\sign(u)=-\sign(p)$. Then, we have that  
		
		\begin{align*}
			u=-\frac{p}{\alpha} - \frac{\beta q}{\alpha} |u|^{q-1}{\sign(\bar u)}&\Rightarrow u\cdot\sign(u)=\frac{p}{\alpha}(-\sign(u)) - \frac{\beta q}{\alpha} |u|^{q-1}\\
			&\Rightarrow |u|= \frac{|p|}{\alpha} - \frac{\beta q}{\alpha} |u|^{q-1}.
		\end{align*}
		
		Therefore, using again \eqref{eq:Phi_ext}, we have that for $|p|\ge|\omega_q|$,
		$$
		\left|-\frac{p}{\alpha} - \frac{\beta q}{\alpha} |u|^{q-1}{\sign(\bar u)} \right|= |u| =\frac{|p|}{\alpha}-\frac{\beta q}{\alpha}|u|^{q-1} \leq \frac{|p|}{\alpha}.
		$$		

		On the other hand, for $w \in L^2(\om)$ we have that $u=\tilde\Phi_q(w)$ belongs to 
		$L^2(\om)$. In fact, due to the last inequality we have that 
		
		\begin{align*}
			\int_\om u(x)^2 dx =& \int_{|w(x)|\geq \omega_q} \tilde\Phi_q(w(x))^2 \,dx\\		
			=& \int_{|w(x)|\geq  \omega_q} \l|-\frac{w(x)}{\alpha} - \frac{\beta q}{\alpha} |u(x)|^{q-1}\sign(u(x)) \r|^2 dx \\
			\leq& \int_{|w(x)|>  \omega_q}  \frac{|w(x)|^2}{\alpha^2}  dx+ c^* |\{x\in\om: w(x)=\omega_q\}| \\
			\leq& \int_{|w(x)|>  \omega_q}  \frac{|w(x)|^2}{\alpha^2}  dx+ c^* |\om|<\infty,
			%				    
		\end{align*}
		%
		where $c^*$ is a positive constant, depending on $\alpha$ and $\omega_q$.
		
		Since the last implies that $\tilde\Phi_q$ is defined from  $L^2(\om)$ into itself, let us consider the generalized system
		
		\begin{equation}\label{eq:monotone_system}
			%
			\l\{
			\begin{array}{lrll}
				&Ay -   \Phi_q(\varphi)  & \ni f,  & \text{ in }  \om,  \\
				&A^*\varphi - y  &= -y_d,  &        \text{ in }   \om,  \\
				& y=\varphi &= 0,  & 	 \text{ on } \ga .
			\end{array}
			\r.
			% 
		\end{equation}
		Let $D(A)=\{v \in H_{0}^{1}(\om): Av \in L^2(\om) \}$ and 
		$D(A^*)=\{v \in H_{0}^{1}(\om): A^*v \in L^2(\om) \}$ the domains of $A$ and $A^*$, 
		respectively, which are densely embeded in $L^2(\om)$. Thus, 
		$A\in \mathcal L(D(A),L^2(\om))$ and therefore $A^*\in \mathcal L(D(A^*),L^2(\om))$ 
		are isomorphisms, see \cite[Section I.4.]{showalter97}; moreover $A$ and $A^*$ are uniformly 
		elliptic by \eqref{eq:coercivity_A}.  Then, according to \cite[Proposition 2.6]{ito-kunisch2014}, $AA^*$ is also a maximal monotone operator with domain
		$$D(AA^*)=\{ v \in H_{0}^{1}(\om): A^*v \in D(A)  \}. $$
		Replacing the first equation of \eqref{eq:monotone_system} into the second, we obtain the generalized equation
		\begin{equation}\label{eq:monotone_phi}
			AA^*\varphi -\tilde\Phi(\varphi) \ni f-Ay_d,
		\end{equation}
		provided that $y_d$ belongs to $D(A)$.
		
		Moreover, $AA^* - \tilde\Phi_q(\cdot) $ is maximal monotone satisfying the coercivity property:
		%
		\begin{align}\label{eq:AA*coer}
			( AA^*\varphi -\tilde\Phi_q(\varphi) ,\varphi )_{L^2(\om)}\geq ( AA^*\varphi  ,\varphi )_{L^2(\om)} \geq c_A \norm{\varphi}^2_{H_{0}^{1}(\om)} , \quad \forall \varphi \in D(AA^*).
		\end{align}
		Hence, as in \cite{ito-kunisch2014} we apply \cite[Corollary 2.3]{brezis} concluding that equation \eqref{eq:monotone_phi} has a solution in $H_{0}^{1}(\om)$, denoted by $\varphi$. According to the  second equation in \eqref{eq:monotone_system}, the state is determined by $y=y_d- A^*\varphi$. In this way, $\varphi$ and $y$ satisfy  \eqref{eq:monotone_system}. 
		
		The case $y_d \in L^2(\om)$ is obtained with the procedure from \cite[Proposition 2.6]{ito-kunisch2014}  using the density of $D(A)$ in $L^2(\om)$. 
		
		In addition, from  \eqref{eq:monotone_phi} and \eqref{eq:AA*coer}  we obtain the bound 
		\begin{align}
			c_A\norm{\varphi}_{H_{0}^{1}(\om)} ^2\leq	(AA^*\varphi,\varphi)_{L^2(\om)} \leq & (f-Ay_d,\varphi)_{L^2(\om)},
		\end{align}
		therefore, there exists some $\kappa>0$ such that 
		\begin{equation}
			\norm{\varphi}_{L^2(\om)} \leq\kappa ( \norm{f}_{L^2(\om)} + \norm{y_d}_{L^2(\om)}).\\
		\end{equation}
		The same estimate is true for $y$ by \eqref{eq:statey_2}, i.e. there exists a constant $\kappa>0$ such that
		\begin{equation}
			\norm{y}_{L^2(\om)} \leq\kappa ( \norm{f}_{L^2(\om)} + \norm{y_d}_{L^2(\om)}).\\
		\end{equation}
		Uniqueness follows from the same arguments as in \cite{ito-kunisch2014}.
		
		\subsubsection*{Global solution of \eqref{eq:OCP}} Let us consider $\bar u \in  \tilde\Phi_q (\varphi)$, % =\tilde  \Phi (\varphi) \in L^2(\om)$. 
		together with $\bar y = S \bar u + y_f$ and $\varphi = S(\bar y -y_d) $, satisfying the first-order necessary conditions. Since, by our assumption, the measure of the set $\{x\in \om : |\varphi(x)|=\omega_q \}$ has zero measure, from \eqref{eq:fonc_H}, we have the condition 
		$$ 0 \leq \frac{\alpha}{2}   u(x)^2 + \beta |  u(x)|^q + \varphi (x)  u(x)-\frac{\alpha}{2} \bar u(x)^2 - \beta |\bar u(x)|^q - \varphi (x) \bar u(x), \quad \forall u  \in L^2(\om)$$ 
		holds for almost all $x\in \om$. From this relation, it follows that 
       \begin{equation}\label{eq:diffnonconvex}
           \beta\int_\om |u(x)|^q \, dx - \beta\int_\om |\bar u(x)|^q \, dx \geq \int_\om \frac{\alpha}{2} \bar u(x)^2 - \frac{\alpha}{2}  u(x)^2\, dx - \int_\om \varphi(x) ( u(x)-\bar u(x)) \, dx.
       \end{equation}

  Thus, taking into account the differentiable terms of the cost function, we have		
		%%$F'(\bar y,\bar u)[v,z] = (\bar y - y_d, S z) +\alpha(\bar u,v)$; therefore,
		\begin{align}
			J(y,u) - J(\bar y,\bar u) = &(\bar y - y_d, S (u-\bar u))_{L^2(\om)} +\alpha(\bar u,u - \bar u)_{L^2(\om)} + \frac{1}{2}\norm{y -\bar y}_{L^2(\om)}^2   \nonumber\\
			&+ \frac{\alpha}{2}\norm{u -\bar u}_{L^2(\om)}^2+ \beta\int_\om |u(x)|^q dx - \beta\int_\om |\bar u(x)|^q dx\nonumber \\
			=&\int_\om (\alpha \bar u(x) + \varphi (x))(u(x)- \bar u(x)) dx + \frac{\alpha}{2}\norm{u -\bar u}_{L^2(\om)}^2 \nonumber\\
			&+ \frac{1}{2}\norm{y -\bar y}_{L^2(\om)}^2 + \beta\int_\om |u(x)|^q dx - \beta\int_\om |\bar u(x)|^q dx, \nonumber
		\end{align}
where we replace \eqref{eq:diffnonconvex} to get
  \begin{align}
			J(y,u) - J(\bar y,\bar u) \geq &\int_\om (\alpha \bar u(x) + \varphi (x))(u(x)- \bar u(x)) dx + \frac{\alpha}{2}\norm{u -\bar u}_{L^2(\om)}^2 \nonumber\\
			&+ \frac{1}{2}\norm{y -\bar y}_{L^2(\om)}^2 + \int_\om \frac{\alpha}{2} \bar u(x)^2 - \frac{\alpha}{2}   u(x)^2 dx \nonumber \\
   &- \int_\om \varphi(x) ( u(x)-\bar u(x)) \, dx \nonumber \\
   = &  \frac{\alpha}{2}\norm{u -\bar u}_{L^2(\om)}^2 + \frac{1}{2}\norm{y -\bar y}_{L^2(\om)}^2  \nonumber\\
   &+  \int_\om  \alpha \bar u(x)(u(x)- \bar u(x) ) +\frac{\alpha}{2} \bar u(x)^2 - \frac{\alpha}{2} u(x)^2 dx \nonumber \\
  =& \frac{1}{2}\norm{y -\bar y}_{L^2(\om)}^2  \geq 0. \nonumber
		\end{align}
		Then, $\bar u$ is a global minimum.
	\end{proof}

	With the estimations provided by Theorem \ref{thm:existence_solution_elliptic_pde} and 
	\eqref{eq:esti_state*_uniform}, we prove that, for enough big value of $\beta$, the global
	solution for \eqref{eq:OCP} is zero.

	\begin{corollary}\label{corollary:null_solution}
		Fix $\alpha>0$ and $0<q<1$. There exists a value $\beta^*>0$, depending on $\alpha$ and $q$ at 
		which, for every $\beta>\beta^*$, the global solution for \eqref{eq:OCP} 
		is zero.
	\end{corollary}

	\begin{proof}
		Let $(\bar y, \bar u)$ a global solution for \eqref{eq:OCP}. Then,
		$$
			\frac{\alpha}{2}\norm{u}_{L^2(\om)}^2\le J(\bar y, \bar u)\le J(0,0)=\frac{1}{2}\norm{y_d}_{L^2(\om)}^2,
		$$
	
	thus 
	\begin{equation}\label{eq:corollary_2_6_1}
		\norm{u}_{L^2(\om)}\le\sqrt{\frac{1}{\alpha}}\norm{y_d}_{L^2(\om)}.
	\end{equation}
	On the other hand, thanks to \eqref{eq:esti_state*_uniform} as well as Theorem 
	\ref{thm:existence_solution_elliptic_pde}, we have that if $\bar \varphi$ is the adjoint state
	which satisfies \eqref{eq:optimal_adjoint} there exists two constants $c_{\infty}^*$ and $c$ such that
	\begin{align*}
		\norm{\varphi}_{L^{\infty}(\om)}&\le c_{\infty}^*\norm{y-y_d}_{L^2(\om)}\\
		&\le c_{\infty}^*(\norm{y}_{L^2(\om)} + \norm{y_d}_{L^2(\om)})\\
		&\le c_{\infty}^*(c\norm{u}_{L^2(\om)} + \norm{y_d}_{L^2(\om)})\\
		&\le \l(c_{\infty}^*c\sqrt{\frac{1}{\alpha}}+c_{\infty}^*\r)\norm{y_d}_{L^2(\om)}.
	\end{align*}
	where the last inequality follows from \eqref{eq:corollary_2_6_1}. So, if we assume that $\jump_q>\l(c_{\infty}^*c\sqrt{\frac{1}{\alpha}}+c_{\infty}^*\r)$,
	by \eqref{eq:null_control} we must have that $\bar u\equiv 0$. Now,
	\begin{align*}
		\jump_q>\l(c_{\infty}^*c\sqrt{\frac{1}{\alpha}}+c_{\infty}^*\r)^{\frac{1}{2-q}}&\Leftrightarrow \l(\frac{2(1-q)\beta}{\alpha}\r)^{\frac{1}{2-q}}>\l(c_{\infty}^*c\sqrt{\frac{1}{\alpha}}+c_{\infty}^*\r)\\	
	&\Leftrightarrow \beta>\frac{\alpha}{2(1-q)}\l(c_{\infty}^*c\sqrt{\frac{1}{\alpha}}+c_{\infty}^*\r)^{2-q}.	
	\end{align*}
	Taking $\beta^*=\frac{\alpha}{2(1-q)}\l(c_{\infty}^*c\sqrt{\frac{1}{\alpha}}+c_{\infty}^*\r)^{2-q}$, the result follows.
	\end{proof}

	
	\section{Partial convexificacion of $(P)$}\label{section:problem_convexification}

	In Subsection 1.3.1 of Chapter 1 we study the $\Gamma$--regularization of function 
	$\phi_q:\mathbb{R}\to [0,+\infty)$, defined as $\phi_q(t) = \alpha t^2 + \beta |t|^q$ for any $q\in(0,1)$. 
	In particular, we shown that its biconjugate coincides with its convex envelope, defined as
	\[
	\phi_q^{**}(t)=\begin{cases}
		\phi(t), & \text{if} \, |t|\ge \jump_q,\\
		\omega_q|t|,   & \text{otherwise},
	\end{cases}
	\]
	according formula \eqref{eq:convex_envelope_phi}, and noting that $t^*=\jump_q$ and
	 $\omega_q=\phi'_q(t)$. Inspired in a reformulation of an optimal control problem of the
	 form \eqref{eq:problem_biconjugate}, and following some ideas of \cite{ito-kunisch2014}, in this 
	section we use the $\Gamma$--regularization of the cost function of \eqref{eq:OCP} to obtain a new
	 optimal control problem, which is convex by properties of the biconjugate of a funtion. Later, 
	we will show that the solution of this problem is also the solution of \eqref{eq:OCP}. The interesting
	fact about this approach is that we can prove the existence of global solutions for \eqref{eq:OCP} following
	a different aproach than the used in the last Section. This show us that the two metodologies: the last one
	based on a maximum principle, and this one based on a convex optimization problem, are equivalent.

We formulate the following convex optimal control problem:
\begin{equation}
		\tag{$\tilde P$} \label{eq:OCP_conv}
		\begin{cases}
			\displaystyle\min_{(y,u)} \tilde J(y,u) := \frac12 \norm{y-y_d}^2_{L^2(\om)} + \int_\om \phi^{**}_q (u(x)) dx \\
			\hbox{ subject to: }\\
			\hspace{40pt}\begin{array}{rll}
				A y(x) =&u(x) + f(x), &\hbox{in  } \om, \\
				y(x)=&0, &\hbox{on  }  \Gamma,
				%\dfrac{\partial y}{\partial \vec{n}}=0&\hbox{sobre  } \Gamma. %, $\gamma= 1e4$,
			\end{array}
			%			\\
			%			\hspace{45pt} u \in L^2(\om),
		\end{cases}   
	\end{equation}

Since $\phi_q^{**}(t)\geq \frac{\alpha}{2}t^2$ according to Proposition \ref{prop:phi**_quadrature}, then any minimizing 
sequence is bounded in $L^2(\om)$. Therefore, the direct method of the calculus of variations implies that 
\eqref{eq:OCP_conv} has a solution in $L^2(\om)$. However, the lack of strict convexity of $\tilde J$ prevents 
its uniqueness.

\subsection{Optimality conditions for \eqref{eq:OCP_conv}} 

The adjoint state is an essential tool to represent optimality conditions. Given an optimal control 
$\tilde u \in L^2(\om)$ for \eqref{eq:OCP_conv} with adjoint state $\tilde \varphi$ solution of the variational 
problem \eqref{eq:costate} with $y=\tilde y = S \tilde u +y_f$, then $\tilde\varphi$ corresponds to the derivative at $\tilde u$ of the function $F(u) = \frac12 \norm{Su-y_d}^2_{L^2(\om)}$ in $L^2(\om)$.

Let $\tilde j(u)= \displaystyle\int_\om \phi_q^{**}(u(x)) dx$ and let $\partial \tilde j$ be its 
subdifferential. If $\tilde{u}$ is an optimal control for \eqref{eq:OCP_conv} then by the Fermat’s principle 
the first-order optimality condition is
$0 \in \tilde{\varphi} \;+\partial \tilde{j} (\tilde{u})$, which we aim to solve for $\tilde{u}$. 
Proceeding formally, notice that $\tilde j$ is proper and weakly lower semicontinuous. Therefore, it 
follows that $\partial \tilde j$ is maximally monotone and its (negative) inverse $\tilde\Phi_q :=-(\partial \tilde j)^{-1}$ is defined as a multifunction. Thus, we can write
$$ \tilde u \in \tilde \Phi_q(\tilde \varphi).$$
The operator $\tilde \Phi_q: L^2(\om) \rightrightarrows L^2(\om) $, was introduced in \cite{ito-kunisch2014} 
for $q=0$ ($L^0$-pseudonorm) through the Pontryagin's maximum principle and using the proximity operator of 
the $\ell_0$ pseudonorm (known in finite dimensions as hard-thresholding). An analogous operator 
$\tilde \Phi_q$, for $q\in (0,1)$, can be defined using the proximity mapping of the function 
$\reals \ni t \mapsto |t|^q$, see \eqref{eq:prox_lq} below. In contrast to the hard-thresholding for
 $q=0$, the corresponding mapping for $q \in (0,1)$ is implicitly defined.  See \cite{bredies2014} 
 for the definition of this mapping in finite dimensions. 

Thus, if $\varphi$ is the adjoint state associated with a control $u$ by equation \eqref{eq:costate}, we denote by $\tilde \Phi_q=-(\partial \tilde j)^{-1}:  L^2(\om) \rightrightarrows L^2(\om)$ which is given by 
%
\begin{equation}\label{eq:Phi_ext_convex}
		%
		\tilde\Phi_q (\varphi)  =	
		%
		\begin{cases}
			-\frac{\varphi}{\alpha}-\frac{\beta}{\alpha} q |u|^{q-1}\sign (u), & \text{ if } |\varphi|>\omega_q, \\
			0,                          &	 \text{ if } |\varphi|<\omega_q, \\
			[-\jump_q, 0] ,                         &	 \text{ if } \varphi=\omega_q,\\
			[0,\jump_q],                         &	 \text{ if } \varphi=-\omega_q.
		\end{cases}
	\end{equation}
    where $\jump_q$ and $\omega_q$ where defined in \eqref{eq:jump_bound}. Figure 2.3 illustrates operators 
	$-\tilde\Phi_q$ for $0\leq q<1$ and $-\tilde\Phi_0$. 

We use $\tilde \Phi_q$ to write the associated optimality system. Let $\tilde u \in L^2(\om)$ be an optimal control for \eqref{eq:OCP_conv}, there exist $\tilde y$ and $\tilde \varphi$ in $H_0^1(\om)$ that satisfy
\begin{subequations}\label{eq:system2.5_convex}
		\begin{align} 
			&	\begin{array}{rll}
				A   \tilde y  =& \tilde u + f, &\hbox{in  } \om, \\
				\tilde y=&0, &\hbox{on  }  \Gamma,
			\end{array} \\
			%	
			&\begin{array}{rll}
				A^*   \tilde\varphi=& \tilde y -y_d, &\hbox{in  } \om, \\
				\tilde \varphi=&0, &\hbox{on  }  \Gamma,
			\end{array}\label{eq:statey_2_convex}\\
			&\tilde u (x) \in \tilde\Phi_q (\tilde\varphi(x)), \quad  \text{a.a. } x \in \om. \label{eq:uPhi.1_convex}
		\end{align} 	
	\end{subequations}
\begin{remark}\label{rmrk:2}
   An optimal solution for $(\tilde{P})$, namely $\tilde {u}$ satisfies system \eqref{eq:system2.5_convex}. Therefore, if $|\tilde{\varphi}(x)|>\omega_q$, then \eqref{eq:Phi_ext_convex} implies that 
   \begin{equation}
   (\alpha|\tilde{u}(x)|+\beta q |\tilde{u}(x)|^{q-1})\sign(\tilde{u}(x))= -\tilde{\varphi}(x). \label{eq:u_phi} %If $\tilde{\varphi}(x)<-\omega_q$, we have that $\tilde{u}(x)>0$. 
   \end{equation}
   Since the continuous function $t\mapsto \alpha t+\beta q t^{q-1}$ is strictly monotone increasing over the interval $[\jump_q,+\infty[$ and that $\omega_q=\alpha \jump_q+\beta q \jump_q^{q-1}$, we have that  the operator $\tilde\Phi_q(\varphi)$ is well defined as a function on the set $\{\ x: |\varphi|>\omega_q\}$ where \eqref{eq:u_phi} is satisfied. Therefore, in this set, $\tilde\Phi_q(\varphi)$ can be evaluated through the solution of the following one-dimensional optimization problem:
   \begin{equation}\label{eq:prox_lq}
   	\min_{t\in \mathbb{R}} \left\{ \frac{\alpha}{2}t^2 + \beta |t|^q + \varphi(x) t \right\}
   \end{equation}
for almost all $x \in \{\ x\in \om: |\varphi(x)|>\omega_q\}$. This is the basis of the Sequential Quadratic Hamiltonian method 
discused in Chapter 3.
   
In the same spirit, it also follows that $|\tilde{u}(x)|>\jump_q$ if, and only if, 
$|\tilde{\varphi}(x)|>\omega_q$, as Lemma \ref{l:thresholds} states. Therefore, we have the following equivalence: 
   %Similarly, if $\tilde{\varphi}(x)>\omega_q$, we have $\tilde{u}(x)<-\jump_q$. Moreover, if $|\tilde{\varphi}(x)|>\omega_q$ then $|\tilde{u}(x)|>\jump_q$. Moreover, if $|\tilde{u}(x)|>\jump_q$, then $|\tilde{\varphi}(x)|>\omega_q$ then $|\tilde{\varphi}(x)|>\omega_q$ by the definition of $\tilde \Phi$. From these relations, it holds the equivalence:
   \begin{equation}\label{eq:equ_sets}
       \Omega_{\jump_q}:=\{x\in \om: |\tilde{u}(x)|>\jump_q\}=\{x\in \om: |\tilde{\varphi}(x)|>\omega_q\}:=\om_{\omega_q}
   \end{equation}
\end{remark}

\subsection{Existence of solutions for \eqref{eq:OCP} via its partial convexification} 

As mentioned in the previous section, there is no guarantee that problem \eqref{eq:OCP} admits a 
solution. Indeed, an analogous counterexample can be constructed by following the arguments presented 
in \cite[Section 4.5]{wachsmuth2019}.Nevertheless, by means of the techniques developed in Section 2.2, 
we establish the existence of a solution to \eqref{eq:OCP} based on a Pontryagin–Hamiltonian principle,
 in the spirit of \cite{ito-kunisch2014}.

Alternatively, one may proceed by proving that, under Assumption \ref{as:phi_zero_measure}, 
every solution of the convexified problem \eqref{eq:OCP_conv} is also a solution of the original 
problem \eqref{eq:OCP}. As pointed out in \cite{ito-kunisch2014}, this strategy is equivalent to 
employing a Hamiltonian principle, which constitutes the main approach adopted in their work.


The following Theorem show us the discused point, i.e., a solution of \eqref{eq:OCP_conv} is also a 
solution of \eqref{eq:OCP}, provided Assumption \ref{as:phi_zero_measure} holds.


\begin{theorem}\label{th:1} 
Let $\bar u$ be a solution for \eqref{eq:OCP_conv}. If $\bar u$ satisfies Assumption \ref{as:phi_zero_measure} then $\bar u$ is the unique solution of \eqref{eq:OCP}.
\end{theorem}
\begin{proof}
Since $\bar u$ is a solution for \eqref{eq:OCP_conv}, there exist states $\bar y = S \bar u + y_f$ and $\bar{\varphi} = S^*(\bar y -y_d) $ that satisfy the first-order necessary conditions \eqref{eq:system2.5_convex}. 

Let us check that $\bar u$ minimizes $J(S\cdot,\cdot)$. By Assumption \ref{as:phi_zero_measure} on the set $\{x\in \om : |\bar{\varphi}(x)|=\omega_q \}$, the integral terms on this set will be neglected in the following estimate. Observe that, by \eqref{eq:uPhi.1_convex}, $\bar u(x)=\tilde\Phi(\bar\varphi(x))=0$ in $\{x:|\bar{\varphi}(x)|<\omega_q\}$.  By the definition of $\phi^{**}$, we have		%%$F'(\bar y,\bar u)[v,z] = (\bar y - y_d, S z) +\alpha(\bar u,v)$; therefore,
		\begin{align}
			J(y,u) - J(\bar y,\bar u)  = &\frac12\|y-y_d\|^2_{L^2(\om)} +\frac{\alpha}{2}\|u\|^2_{L^2(\om)} + \beta \int_{\om}|u(x)|^q\,dx  \nonumber \\
			&-\frac12\|\bar y-y_d\|^2_{L^2(\om)} -\frac{\alpha}{2}\|\bar u\|^2_{L^2(\om)} - \beta \int_{\om}|\bar u(x)|^q\,dx \nonumber \\
			=&\frac12\|y-y_d\|^2_{L^2(\om)} + \int_{\om}\phi^{**}(u(x))\,dx -\frac12\|\bar y-y_d\|^2_{L^2(\om)} -\int_{\om}\phi^{**}(\bar u(x))\,dx  \nonumber \\
			& -\int_{{|u|<\jump_q}} \omega_q |u(x)| dx + \int_{{|u|<\jump_q}} \frac{\alpha}{2}|u(x)|^2 + \beta |u(x)|^q  dx\nonumber\\
			=& \tilde J(y,u) - \tilde J(\bar y,\bar u) -\int_{{|u|<\jump_q}} \omega_q |u(x)| dx + \int_{{|u|<\jump_q}} \frac{\alpha}{2}|u(x)|^2 + \beta |u(x)|^q  dx. \label{eq:J-J-1}
		\end{align}
%
By assumption, $\bar u$ minimizes $\tilde J(S \cdot +y_f,\cdot)$, therefore \eqref{eq:J-J-1} implies: 
\begin{equation}
J(y,u) - J(\bar y,\bar u) \geq \int_{{|u|<\jump_q}} -\omega_q |u(x)|+\frac{\alpha}{2}|  u(x)|^2 + \beta |u(x)|^q  dx. \label{eq:J-J-1a}	
\end{equation}
%
We analyze the integrand of the last term as follows:
\begin{align}
	\omega_q|u(x)| = & \alpha \frac{2-q}{2-2q} ((1-q)\frac{\beta}{\alpha})^{\frac{1}{2-q}} |u(x)|
				   = \frac{2-q}{2-2q} |u(x)|^q  \alpha^{\frac{1-q}{2-q}} |u(x)|^{1-q}((1-q)\beta)^{\frac{1}{2-q}}.	\label{eq:J-J-1b}
\end{align}
Using the Young's inequality for $p=\dfrac{2-q}{1-q}$ and $p'=2-q$ (satisfying $1/p+1/p' =1$), we obtain:
\begin{align}
	\alpha^{\frac{1-q}{2-q}} |u(x)|^{1-q}\, ((1-q)\beta)^{\frac{1}{2-q}} \leq & \frac{1}{p}(\alpha^{\frac{1-q}{2-q}} |u(x)|^{1-q})^p + \frac{1}{p'}((1-q)\beta)^{\frac{p'}{2-q}}\nonumber\\
	\leq &\alpha |u(x)|^{2-q} \dfrac{1-q}{2-q}+\dfrac{1-q}{2-q}\beta \label{eq:J-J-2}.
\end{align}
Now, we replace \eqref{eq:J-J-2} into \eqref{eq:J-J-1b}, which gives:
%
\begin{align}
	-\omega_q|u(x)| \geq &  -\frac{1}{2}\frac{2-q}{1-q} |u(x)|^q  \l(	\alpha |u(x)|^{2-q} \dfrac{1-q}{2-q}+\dfrac{1-q}{2-q}\beta\r)\nonumber\\
	=&-\dfrac{\alpha}{2} |u(x)|^{2}-\frac{\beta}{2}|u(x)|^{q} \ge -\dfrac{\alpha}{2} |u(x)|^{2}- {\beta}|u(x)|^{q}.
\end{align}
By replacing this relation in \eqref{eq:J-J-1a}, we deduce that $\bar u$ is a global minimum. The uniqueness follows from the same arguments as in \cite{ito-kunisch2014}.
\end{proof}

\begin{remark}\label{r:u_prop} 
	Under Assumption 	\ref{as:phi_zero_measure}, if $\bar u \in L^2(\om)$ is the solution for 
	\eqref{eq:OCP_conv}, there exist $\bar y =S\bar u +y_f$ and $\bar\varphi$ in $H_0^1(\om)$ which satisfy
	 the state equation \eqref{eq:variational_formulation} and \eqref{eq:costate}, respectively and moreover 
	 the relation \eqref{eq:uPhi.1_convex} reduces to: 
\begin{equation}\label{eq:Phi2_convex}
			%
			\bar u=\Phi_q (\bar\varphi) =	
			%
			\begin{cases}
				-\frac{\bar\varphi}{\alpha}-\frac{\beta}{\alpha} q |\bar u|^{q-1}\sign (\bar u), & \text{ if } |\bar\varphi|> \omega_q, \\
				0,                         &	\text{ otherwise.}
			\end{cases}
		\end{equation}
This relation also implies that
\begin{equation}\label{eq:phi_q_eval_u}
\phi_q^{**}(\bar u(x)) = \phi_q(\bar u(x)), \quad \text{for almost all } x \in \om.
\end{equation}
The latter yields that $\tilde J(S\bar u,\bar u) = J(S\bar u,\bar u) \leq J(S  u,  u) \leq \tilde J(S\bar u,\bar u)$, for all $u$; i.e. $\bar u$ is a minimizer of $\tilde J(S\cdot,\cdot)$. 

In addition, if $q \to 0$ we have
	$
		%
		\Phi_q (\cdot)  \arrow 	\Phi_0(\cdot):=
		%
		\begin{cases}
			-\frac{(\cdot)}{\alpha}, & \text{ if } |\cdot|> \omega_0=\sqrt{2\alpha\beta}, \\
			0,                         &	\text{ otherwise,}
		\end{cases},
	$
	where $\Phi_0$ is precisely the operator defined in \cite{ito-kunisch2014} for the $L^0(\om)$-pseudonorm under Assumption \ref{as:phi_zero_measure}.          
\end{remark}
Thus, $|\bar u|$ is bounded away from 0 in its support, and $\jump_q$ in 
\eqref{eq:jump_bound} estimates the jump discontinuity. Figure 
\ref{fig:jump} depicts the behavior of $\jump_q$ as a function of $q$ for fixed $\alpha$ and $\beta$. We also observe the convergence of $\jump_q$ to $\jump_0=\sqrt{\frac{2\beta}{\alpha}}$ (when $q\to 0$), corresponding to the jump value of the $L^0(\om)$-pseudonorm $\jump_0=\sqrt{\frac{2\beta}{\alpha}}$. For certain ratios $\beta/\alpha$,  $\jump_q$ can reach larger values than the corresponding $\jump_0$.

	
\section{Incorporating box-constraints on the controls}
Let us briefly discuss the modifications of the previous results to incorporate control constraints. Let \(u_a\) and \(u_b\) be real numbers such that \(u_a \leq 0 \leq u_b\) with \(u_a \ne u_b\). We define the set \(U = \{t \in \mathbb{R} : u_a \leq t \leq u_b\}\),  and  
\begin{equation}\label{eq:Uad} 
	 u \in U_{ad}= \{ v \in L^2(\om): v(x) \in U, \, \text{ for almost all }x\in \om \}. 
\end{equation}
Then, the maximum principle is applied to the extended Hamiltonian:
\begin{equation} 
\mathcal H(x,y,u,p)= \frac{1}{2}|y-y_d(x)|^2 + \frac{\alpha}{2}u^2 + \beta |u|^q + pu + \mathcal{I}_{U}(u),	\nonumber
\end{equation}
which leads to the optimization	problem \eqref{eq:1dlq}, restricted to the interval $[u_a,u_b]$. Therefore, its solution can be expressed in terms of the projection on the interval $[u_a,u_b]$; that is:
\begin{equation}\label{eq:1dlqc}
		\bar u \displaystyle\in  \argmin_{u\in [u_a,u_b]} \left\{ \frac{\alpha}{2}u^2+\beta |u|^q + pu \right\},
	\end{equation}
Then, the constrained optimal control problem is formulated by
\begin{equation}
		\tag{$ P_{U_{ad}}$} \label{eq:OCP_c}
			\displaystyle\min_{(y,u)} J(y,u) = \frac12 \norm{y-y_d}^2_{L^2(\om)} + \int_\om \phi_q(u) \, dx, \qquad \text{subject to: } \, u\in U_{ad},
\end{equation}
where $y$ is a solution of the state equation \eqref{eq:variational_formulation}. The partially 
convexified optimal control problem with control constraints, denoted by 
$(\tilde P_{U_{ad}})$, is considered as well by replacing $\phi_q$ by $\phi_q^{**}$.



We have learned from the unconstrained case that $|\bar u(x)|>\jump_q>0$ or $\bar u (x)=0$. Therefore, for simplicity, we further assume that $u_a < - \jump_q<0<\jump_q<u_b$. Therefore, the solution $\bar u $ is characterized by 
\begin{equation}\label{eq:Phi2_c}
			%
	\bar u=		\mathcal{P}_{[u_a,u_b]}(\Phi_q (p)) =	
			%
			\begin{cases}
			u_a, &  \text{ if } -p\leq  p_a, \\
			u_b, &  \text{ if } -p\geq  p_b, \\
				-\frac{p}{\alpha}-\frac{\beta}{\alpha} q |\bar u|^{q-1}\sign (\bar u), & \text{ if } \omega_q<|p|,\,  \text{ and } p_a<-p<p_b  , \\
				0,                         &	\text{ otherwise.}
			\end{cases}
\end{equation}
where $p_a : = \alpha u_a -  \beta q  |u_a|^{q-1}<0$	 and $p_b= \alpha u_b +  \beta q  |u_b|^{q-1}>0$. 

It is clear that  $-\mathcal{P}_{[u_a,u_b]}(\Phi_q (p))	$ is also a monotone operator. The projection applied in \eqref{eq:Phi2_c} truncates $-\Phi(x)$ to the interval $[u_a,u_b]$; hence, $- \mathcal{P}_{[u_a,u_b]}(\tilde\Phi_q (p))$ is also maximal monotone. Therefore, Theorem \ref{t:existence} is also valid when optimal control problem includes box-constraints of the form \eqref{eq:Uad}. 

The optimality system for the box-constrained case reads: let $\bar u$ be an optimal 
control for problem $(P)$ with control constraints \eqref{eq:Uad}; then, there exist 
$\bar y \in H_{0}^{1}(\om)$ and $\varphi \in \rm{H}^2(\om)$ such that the following system is satisfyed:

\begin{subequations}\label{eq:system_box}
		\begin{align} 
			&	\begin{array}{rll}
				A \bar y=& \bar u + f, &\hbox{in  } \om, \\
				\bar y=&0, &\hbox{on  }  \Gamma,
			\end{array} \\
			%	
			&\begin{array}{rll}
				A^*   \varphi=& \bar y -y_d, &\hbox{in  } \om, \\
				\varphi=&0, &\hbox{on  }  \Gamma,
			\end{array}\\
			& \alpha \bar u (x) + \beta q |\bar u(x)|^{q-1} \sign(\bar u(x)) + \varphi(x)  = 0, \\
			& \quad a.a. \, x \in \{x: |\varphi(x)|>\omega_q \text{ and }  p_a<-\varphi(x)<p_b \},\nonumber\\
			& \bar u(x) =0, \quad \text{a.a. }  \, x \in \{x: \,  |\varphi(x)| \leq \omega_q\}, \\
			& \bar u(x) = u_a, \quad \text{a.a. } x \in \{x: -\varphi(x) \leq p_a\}, \\
			& \bar u(x) = u_b, \quad \text{a.a. } x \in \{x: -\varphi(x) \geq p_b\}.
		\end{align} 	
	\end{subequations}
	
As in the unconstrained case, this system might not be solvable if the measure of the set $\{x\in\om:|\varphi(x)|=\omega_q\}$ is not null. Moreover, the solution $\bar u \in U_{ad}$ is also the solution to the constrained convexified optimal control problem:

 \begin{equation}
		\tag{$\tilde P_C$} \label{eq:OCP_conv_c}
		\begin{cases}
			\displaystyle\min_{(y,u)} \tilde J(y,u) := \frac12 \norm{y-y_d}^2_{L^2(\om)} + \int_\om \phi_q (u(x)) \; dx \\
			\hbox{ subject to: }\\
			\hspace{40pt}\begin{array}{rll}
				A y(x) =&u(x) + f(x), &\hbox{in  } \om, \\
				y(x)=&0, &\hbox{on  }  \Gamma,
				%\dfrac{\partial y}{\partial \vec{n}}=0&\hbox{sobre  } \Gamma. %, $\gamma= 1e4$,
			\end{array}
						\\
						\hspace{45pt} u \in U_{ad}.
		\end{cases}
	\end{equation}

 \section{Incorporating mixed control--state constrains}

 Optimal control problems which present restrictions over the control and state are studied by 
 several authors, see for example \cite{casas, casas1993, casas-mateos2002, casas2008}, etc. 
 Those problems are important in practical uses, for example, problems involved with heat phenomena, 
 elasticity theory, flux theory, finances and over all problems which demands that the state must be 
 in specific set \cite{hintkun}. However, when we impose point-wise state constrains in some 
 optimal control problems with convex cost function, it was shown that the Lagrange multipliers 
 that appears in the optimal systems have poor regularity, see for example 
 \cite{casas, casas2008}. This result introduces a new challenge in the study of this kind 
 of problems, because the lack of sufficient regularity for the Lagrange multipliers arisen from the 
 optimal system above implies that their numerical treatment could be difficult. 
 Even the active-set strategies proposed by Bergounioux, Ito and Kunisch \cite{bik}, Bergounioux and 
 Kunisch \cite{bk}, or Kunisch and Rosch \cite{kr}, cannot be applied for its numerical treatment. 
 However, in \cite{meyer-2007} it is introduced a technique for witch we get a sub problem with $L^2$ 
 Lagrange multipliers. This technique consists in defining an artificial control which involves the 
 originals states and control of the problem and reformulate the original optimal control problem 
 with the new artificial control. This process is called a \textit{Lavrentiev regularization} for 
 the problem, and the main idea of this is to interchange the point-wise constrains from the 
 original state to the new defined control.

 In this section we study a certain type of optimal control problem which presents a $L^q$ quasi 
 norm penalization, $q\in (0,1)$, and mixed control and state point-wise constraints;
  being these restrictions inspired in a Lavrentiev-type mix of control and state point-wise 
  restrictions. Specifically, we demonstrate that our problem has a solution which can be used 
  for the study of another control problem with a $L^q$ penalization and pure state point-wise 
  state constraints. Then, we derive an optimal system for the penalized problem with pure state 
  point-wise constraints, using the theory of Difference of Convex functions. 

 For given real positive constants  $\alpha$, $\beta$, $\lambda$ and $q\in (0,1)$ and $\lambda>0$, we are interested in the mixed control-state constrained optimal control problem:
\begin{equation}\label{plambda}\tag{$P_{\lambda}$}
    \begin{cases}
    \displaystyle\min_{(y,u)\in H^1(\om)\times L^2(\om)}\; J(y,u) := \frac{1}{2}\norm{y-y_d}^2_{L^2(\om)}+\frac{\alpha}{2}\norm{u}^2_{L^2(\om)}+\beta \int_{\om} |u|^{q}\; dx\\
    \mbox{subject to:}\\
    Ay(x)=u(x), \phantom{aaaaa} \mbox{in } \om,\\
    y(x)=0, \phantom{aaaaaaaaaaaaa} \mbox{over } \Gamma,\\    
    y_a\le y(x)+\lambda u(x)\le y_b,\phantom{a} \mbox{almost all }x\in \Omega
    \end{cases}
\end{equation}
with $y_a, y_b$ real constants. 

\begin{remark}
    Mixed constraints are also motivated by the Lavrentiev type regularization in the 
	presence of point-wise state constrains, see \cite{meyer-2007}. 
    The main reason behind this consideration can be explained as follows: first of all, 
	if we define the problem $(P_0)$ as same as the problem $(P_{\lambda})$, except for 
	the point-wise constraints that we replace by 
	$$y_a\le y(x)\le y_b,\quad \text{for all } x\in \Omega.$$
    
     Thus, $P_{0}$ is a non convex problem with point-wise state constraints. Such problems 
	 are practically and theoretically interesting due to the optimal control sparsity 
	 properties and the applicability of the state constraints. However, since the cost 
	 function is not convex as we have discussed before, the existence of a solution for $P_0$ 
	 cannot be followed by the usual direct methods. One possible strategy is the use of the
	 $\Gamma$--regularization in problem \eqref{plambda}, as in the case of \eqref{eq:OCP} studied in
	 Section \ref{section:problem_convexification}
\end{remark}

\subsection{Convex relaxation of \eqref{plambda}}

We recall that in absence of state constraints, or mixed control--state constraints, 
the optimality system that arises defines a monotone operator that depends on 
the optimal variables, see details of Theorem \ref{t:existence}. However, the consideration of state 
constraints complicate the description of the associated optimality system by 
means of a monotone operator. Therefore, we rely on a convex relaxation $(P^C_\lambda)$ of the problem 
$(P_\lambda)$, for which we can establish the existence of solutions. Under similar hypotheses regarding 
the structure of the adjoint state as in Assumption \ref{as:phi_zero_measure}, we demonstrate that a 
particular solution of the relaxed optimal control problem indeed solves $(P^C_\lambda)$. Details are as 
follows. First of all, we introduce the convex optimal control problem as the convex relaxation of $(P_\lambda)$: 
    \begin{equation}\label{convex}\tag{$P^C_{\lambda}$}
    \begin{cases}
    \displaystyle\min_{(u,y)\in L^2(\om)\times H^1(\Omega)} \; J^C(y,u):=\frac{1}{2}\norm{y-y_d}^2_{L^2(\om)}+\int_{\Omega}\phi_q^{**}(u)\; dx\\
    \mbox{subject to:}\\
    Ay(x)=u(x), \phantom{aaaaa} \mbox{in } \om,\\
    y(x)=0, \phantom{aaaaaaaaaaaaa} \mbox{over } \Gamma,\\    
    y_a\le y(x)+\lambda u(x)\le y_b,\phantom{a} \mbox{almost all }x\in \Omega
    \end{cases}
    \end{equation}

Notice that, as same as in \eqref{eq:OCP}, \eqref{convex} has a  cost function that
 is convex, continuous and bounded-from-below. These properties allow us to apply the 
 direct method. Due to the mixed constrains, we explicitly demonstrate the result below.
\begin{lemma}\label{lemma:existence_solution_PClamb}
       Problem \eqref{convex} has a solution in $L^2(\om)$.
\end{lemma}
 
  \begin{proof}
   Let $\{(u_k,y_k)\}_{k\in \mathbb{N}}\in L^2(\Omega)\times H_0^1(\Omega)$ a minimizing and 
   admissible sequence for \eqref{convex}, i.e., for each $k$, $y_k \in H^1(\Omega)$ satisfies 
   the state equation with associate control $u_k \in L^2(\om)$. Moreover, the pair $(u_k,y_k)$ 
   satisfies the mixed-constraints:
    \[
    y_a\le y_k(x)+\lambda u_{k}(x)\le y_b,
    \]
	The minimizing sequence $\{(u_k,y_k)\}_{k\in \mathbb{N}}$ is bounded. Indeed, 
	$\{u_k\}_{k\in \mathbb{N}}$ is bounded in $L^2(\Omega)$  due to the presence of the 
	Tikhonov penalizer $\frac{\alpha}{2}\norm{u}_{L^2(\Omega)}^2$ in the cost function, with 
	$\alpha>0$. Moreover, thanks to the estimate in Theorem \ref{thm:existence_solution_elliptic_pde} 
	we have that: 
	$$ 
	\norm{y_k}_{H^1(\Omega)}\leq c_A \norm{u_k}_{L^2(\Omega)},
	$$
	which shows that $\{y_k\}_{k\in \mathbb{N}}$ is bounded in $H^1(\om)$.

	Therefore, there exists  a subsequence (without renaming) of 
	$(y_k,u_k)_{k\in\mathbb{N}}$  such that 
	$(y_{k},u_{k})\rightharpoonup (\hat{y},\hat{u})$ in 
	$H_0^1(\Omega)\times L^2(\Omega)$. Moreover, it is known by the compact 
	embedding $H_0^1(\Omega) \hookrightarrow \hookrightarrow L^2(\Omega)$ that 
	the weakly convergence of $y_k$ to $\hat{y}$ in $H_0^1(\Omega)$ implies that 
	$y_{k}\to y$ strongly in $L^2(\Omega)$ as $k\to \infty$. Thus,  we can pass 
	to the limit $k\to \infty$ in the weak formulation in 
	\eqref{eq:variational_formulation}, obtaining that
	 \[
        a(\hat y, v)=\lim_{k\to\infty}a(y_k,v) = \lim_{k\to\infty}(u_k,v)_{L^2(\Omega)}=(\hat u,v),\quad \forall v \in H_0^1(\Omega),
    \]
	implying that the weak limit $(\hat y,\hat u)$ satisfies the state equation.
	On the other hand, the weak convergence  $u_k \rightharpoonup \hat u$, and
	the strong convergence $y_k \to \hat y$ in $L^2(\Omega)$ imply that, for 
	any $\lambda>0$, $y_k+\lambda u_k\rightharpoonup \hat{y}+\lambda\hat{u}$ 
	weakly in $L^2(\om)$. In view that the set 
	\[
		U_{ad}:=\{v\in L^2(\om ):y_a\le u(x)\le y_b \mbox{ almost all }x\in \om\}
	\]
	is a closed and convex set in $ L^2(\Omega)$ and thus weakly closed in 
	$L^2(\om)$, then $\hat{y}+\lambda\hat{u}\in U_{ad}$. This shows that the 
	limit points $(\hat{u},\hat{y})$ are also feasible for the problem.  
	Let us denote $\hat{J}=\inf_{(y,u)} J^{C}(y,u)$. The convexity and 
	continuity of $J$ imply that $J$ is a weakly lower semicontinous functional. 
	Therefore,
     \[
       \hat{J}=\lim_{n\to \infty}J^{C}(y_{k_n},u_{k_n})\ge \liminf_{n\to \infty}J(y_{k_n},u_{k_n})\ge J^{C}(\hat{y},\hat{u}),
    \]
       thus $(\hat{y},\hat{u})$ minimizes $J$.
   \end{proof}

   \subsection{Optimality conditions for the relaxed problem $(P^C_\lambda)$}

   Recll the definition of operator $S$ presented in Remark \ref{rmrk:operator_S}, which, for each
   $u\in L^2(\om)$ it asigns the solution $y=Su$ to \eqref{eq:variational_formulation}. Using the 
   compact embedding $E:H_0^1(\Omega) \to L^2(\Omega)$ we define $R: L^2(\om) \to  L^2(\om)$ by $R=ES$. 
   Now, since  $R$ is invertible we introduce the Fredholm operator  
$$B_{\lambda}:L^{2}(\om)\to L^{2}(\om), \qquad \text{by} \qquad B_\lambda =(R+ \lambda I)^{-1},$$ 
\begin{equation} \label{eq:B_Lamb1}   
B_{\lambda}v=B_{\lambda}(y+\lambda u)=(\lambda I+R)^{-1}(\lambda I+R)u=u.
\end{equation}
Notice that $R$ is a compact operator; thus, $B_\lambda$ is a Fredholm operator that has only countable 
many eigenvalues accumulating at $0$ \cite{meyer-2007}.

Following a similar idea presented in\cite{meyer-2007}, we make the following change of variable:  
$v=y+\lambda u$. Thus, by using \eqref{eq:B_Lamb1} the problem $(P^C_\lambda)$ 
can reformulated as a reduced optimization problem with control constraints:
\begin{subequations}\label{eq:reduced}
\begin{align}%\label{reduced}
    &\min_{v\in L^2(\Omega)}\frac{1}{2}\norm{SB_{\lambda}v-y_d}_{L^2(\om)}^2+\int_{\om}\phi_{q}^{**}(B_{\lambda}v), \label{eq:reduced_PClamb} \\
    & \text{ subjec to : } v \in V_{ad}=\{v\in L^2(\om): y_a\le v(x)\le y_b, \text{ almost all }x\in \om\} \label{eq:boxconst_PClamb}.
\end{align}
\end{subequations}


Optimality conditions for problem \eqref{eq:reduced} are obtained by using the Fermat's principle applied to the convex function 
$$F(v)= \frac{1}{2}\norm{SB_{\lambda}v-y_d}_{L^2(\om)}^2+ G(B_\lambda v) + \mathbf{I}_{V_{ad}}(v), \quad \text{with} \quad G(u) = \int_\om \phi_{q}^{**}(u) dx.$$
Here, for any Hilbert space $X$, and $U\subset X$, the function $\mathbf{I}_{U}:X\to\{0,+\infty\}$ is the 
indicator function of the set $U$, i.e., 

$$
\mathbf{I}_{U}(x)=\begin{cases}
0, & x\in U,\\
+\infty, & x\notin U.
\end{cases}
$$

Therefore, in view of the the calculus rules for subdifferentials of convex functions,  the solution  $\bar v$ of \eqref{eq:reduced} is characterized by the inclusion: 

\begin{equation}\label{eq:oc_v}
0 \in \partial F (\bar v)= B_\lambda^*S^*(SB_\lambda \bar v -y_d) + B_\lambda^* \partial G(B_\lambda \bar v) + \partial \mathbf{I}_{V_{ad}}(\bar v).
 \end{equation}


The condition \eqref{eq:oc_v} is sufficient to obtain the optimality conditions for problem 
\eqref{eq:reduced}.	The following Theorem gives these conditions.

\begin{theorem}
    Let $\bar{u}\in L^{2}(\Omega)$ an optimal control for problem 
	\eqref{convex}, and $\bar{y}$ its associated optimal state. There 
	exists $\overline{\phi}\in H_0^1(\Omega)$, $\mu_a, \mu_b, \zeta\in L^2(\Omega)$ such that the following optimal system is full-filled:    
	\begin{equation}\label{optimality_convex}
        \begin{split}         
        &A\bar{y}=\bar{u}, \hspace{3.5cm} \mbox{in }\Omega\\
        &\bar{y}=0, \hspace{3.45cm} \mbox{on }\Gamma,\\
        &A^*\overline{\phi}=\bar{y}-y_d+\mu_b-\mu_a, \qquad \mbox{in }\Omega,\\
        &\overline{\phi}=0,\hspace{3.5cm}\mbox{on }\Gamma,\\        
        &\overline{\phi}+\zeta+\lambda(\mu_b-\mu_a)=0,\\
        &\mu_a, \mu_b\ge 0,\\
        &\mu_a(\lambda \bar{u}+\bar{y}-y_a)=\mu_b(\lambda \bar{u}+\bar{y}-y_b)=0,\\
        &\zeta(x)=\begin{cases}
            \alpha \bar{u}(x)+\beta q |\bar{u}(x)|^{q-1}\sign(\bar{u}(x)), &|\bar{u}(x)|\ge \jump_q,\\
            r^*\sign(\bar{u}(x)), &|\bar{u}(x)|<\jump_q, |\bar{u}(x)|\ne 0,\\
            \eta \in [-\omega_q,\omega_q],& |\bar{u}(x)|=0.
        \end{cases}  
        \end{split}
    \end{equation}    
\end{theorem}
\begin{proof}
    Let $\overline{v}$ the optimal control for \eqref{eq:reduced}, whose existence 
	can be deduced from the convexity of the cost function in this problem, the 
	structure of the feasible control set, the properties of the linear operators 
	$S$ and $B_{\lambda}$, and following similar steps as in Lemma \ref{lemma:existence_solution_PClamb}. 
	Now, for any $\zeta\in \partial G(\overline{v})$, by \eqref{eq:subb_lp_integrand} 
	we have that $\zeta\in L^2(\Omega)$ and moreover it can be compute explicitely.
	 On the other hand, $\overline{\phi}$ is the solution of the adjoint equation 
	 $A^*\overline{\phi}=\bar{y}-y_d$, so $\overline{\phi}\in L^2(\om)$ and therefore 
	 $\overline{\phi}+\zeta \in L^2(\Omega)$. 
	 
	 Now, define $\mu_a:=[B_{\lambda}^*(\overline{\phi}+\zeta)]_+$ 
	 and $\mu_b:=[B_{\lambda}^*(\overline{\phi}+\zeta)]_-$. Accordingly to the the 
	 definition of the operator $B_{\lambda}$ and the positive and negative parts of a 
	 function, we have that $\mu_a, \mu_b\in L^2(\om)$. Using a well-known result about control 
	 problems with box constrains over the optimal control, (see for example \cite{troeltzsch2010}), 
	 we have that $\mu_{a}(\overline{v}-y_a)=\mu_b(\overline{v}-y_b)=0$ almost all $x\in \om$, and moreover 
   \[
   \overline{\phi}+\zeta+\mu_b-\mu_a=0,
   \]
   where $\zeta\in \partial G(B_{\lambda}\overline{v})$, and $\overline{v}$ the optimal control for \eqref{eq:reduced}. From here, it is easy to recover the original optimal system for \eqref{convex}, using the the definition of $B_{\lambda}$ and the calculus rules for the convex subdifferentials (see \cite{combettes}). In fact, due to the relation $\bar{u} = B_\lambda \bar v$ and since $\overline{v}$ is an optimal solution for \eqref{eq:reduced}, we deduce that $\bar{u}$ is optimal for \eqref{convex}, and therefore, its associated state $\bar{y}:=R\bar{u}$, is optimal state for \eqref{convex}. Now, the composition of $F$ with a linear operator calculus rule tell us that 
\begin{equation}\label{eq:oc_u}
    0 \in B_\lambda^*(\bar \phi + \partial G(\bar u)) + \mu_b-\mu_a.
\end{equation}
Due to the inverbility of $B_{\lambda}$, \eqref{eq:oc_u} is equivalent to
\[
\bar \phi+\zeta+B^{-*}_{\lambda}(\mu_b-\mu_a)=0.
\]
Using the fact that $\overline{v}=\lambda\bar{u}+\bar{y}$, the complementary conditions $\mu_{a}(\overline{v}-y_a)=\mu_b(\overline{v}-y_b)=0$ are changed to $\mu_a(\lambda\bar{u}+\bar{y}-y_a)=\mu_b(\lambda\bar{u}+\bar{y}-y_b)=0$. Finally, since $B^{-*}_{\lambda}(\mu_b-\mu_a)=\lambda(\mu_b-\mu_a)+R^*(\mu_b-\mu_a)$, the linearity of $R^*$ and the definition of the adjoint state allow us to complete the demonstration.
\end{proof}

\subsection{Existence of solutions for the non convex problem}

The last Theorem provide us candidates for optimal solutions to \eqref{plambda}. The following result 
allow us to demonstrate that a solution for \eqref{convex}, under suitable conditions chosen from the 
optimal system \eqref{optimality_convex}, is, in fact, an optimal solution for the original problem. 
Details are as follows.

\begin{theorem}
    Let $(\bar{y},\bar{u})$ an optimal solution for \eqref{convex} and assume that the set 
	$\om^*:=\{x\in \om: 0<|\bar{u}(x)|<\jump_q\}$ has zero measure. Then, $(\bar{y},\bar{u})$ is a 
	solution for $\eqref{plambda}$.
\end{theorem}
\begin{proof}
    Pick up any $(y,u)\in H^{1}(\om)\times L^2(\om)$ feasible for \eqref{plambda}. A standard computation 
	show us that
     \begin{equation}\label{eq1:theorem2}
     \begin{split}
        J(y,u)-J(\bar{y},\bar{u})=&(\bar{y}-y_d, R(u-\bar{u}))_{L^2(\Omega)}+\alpha(\bar{u},u-\bar{u})_{L^2(\Omega)}\\
        &+\frac{1}{2}\norm{y-\bar{y}}_{L^2(\om)}^2+\frac{\alpha}{2}\norm{u-\bar{u}}_{L^2(\om)}^2\\
        &+\beta\left(\int_{\Omega}|u(x)|^q\; dx-\int_{\om}|\bar{u}(x)|^q\; dx\right).
        \end{split}
    \end{equation}

    Now, due to the third and fifht equation of \eqref{optimality_convex} we have that
    \begin{align*}
        (\bar{y}-y_d, R(u-\bar{u}))_{L^2(\Omega)}&=(\overline{\phi}, u-\bar{u})_{L^2(\Omega)}-(\mu_b-\mu_a,R(u-\bar{u}))_{L^2(\Omega)}\\
        &=(-\zeta-\lambda(\mu_b-\mu_a),u-\bar{u})_{L^2(\om)}-(\mu_b-\mu_a,R(u-\bar{u}))_{L^2(\Omega)}\\
        &=(-\zeta,u-\bar{u})_{L^2(\om)}-(\mu_b-\mu_a,\lambda(u-\bar{u}))_{L^2(\om)}\\
        &\phantom{=-}-(\mu_b-\mu_a,y-\bar{y})\\
        &=(-\zeta,u-\bar{u})_{L^2(\om)}-(\mu_b-\mu_a,\lambda u+y-\lambda \bar{u}-\bar{y})_{L^2(\om)},
    \end{align*}
  where the third equation above corresponds to the identity $Ru=y$ and $R\bar{u}=\bar{y}$, which is 
  verified since $(y,u)$ is admissible for \eqref{plambda} and $(\bar{y},\bar{u})$ is the solution for 
  \eqref{convex}. Now, suppose that almost all $x\in \om$, $y_a<\lambda u(x)+y(x)<y_b$. Then, due to the 
  complementary contidions in the seventh equation in \eqref{optimality_convex} we have that 
  $\mu_a(x)=\mu_b(x)=0$, so in this subset of $\om$ we have that 
  $(\bar{y}-y_d, R(u-\bar{u}))_{L^2(\Omega)}=(-\zeta,u-\bar{u})_{L^2(\om)}$. Consider now the set of almost 
  all $x\in \om$ such that $\lambda \bar{u}(x)+\bar{y}(x)=y_b$. Then, again by the complementary equations 
  we have that $\mu_a=0$. But, since $(\bar{y},\bar{u})$ is feasible for \eqref{plambda}, we have that 
  $\lambda u(x)+y(x)-y_b\le 0$, so in this subset of $\om$, 
  $(\mu_b-\mu_a,\lambda u+y-\lambda \bar{u}-\bar{y})_{L^2(\om)}\le 0$. Finally, for all $x\in \om$ such 
  that $\lambda \bar{u}(x)+\bar{y}(x)=y_a$, we have that $\mu_a=0$ accordingly the 
  complementary conditions mentioned before. The feasibility of $(y,u)$ again tell us 
  that $\lambda u(x)+y(x)-y_a\ge 0$ so in this set we have again 
  $(\mu_b-\mu_a,\lambda u+y-\lambda \bar{u}-\bar{y})_{L^2(\om)}\le 0$. Therefore, we conclude that for almost all $x\in \om$,
  \[
  (\mu_b-\mu_a,\lambda u+y-\lambda \bar{u}-\bar{y})_{L^2(\om)}\le 0,
  \]
  and therefore
  \[
  (\bar{y}-y_d, R(u-\bar{u}))_{L^2(\Omega)}\ge (-\zeta,u-\bar{u})_{L^2(\om)}.
  \]
  The last inequality show us that \eqref{eq1:theorem2} changes to the relation
  \begin{equation}\label{eq2:theorem2}
     \begin{split}
        J(y,u)-J(\bar{y},\bar{u})\ge&(\alpha\bar{u}-\zeta,u-\bar{u})_{L^2(\Omega)}\\
        &+\frac{1}{2}\norm{y-\bar{y}}_{L^2(\om)}^2+\frac{\alpha}{2}\norm{u-\bar{u}}_{L^2(\om)}^2\\
        &+\beta\left(\int_{\Omega}|u(x)|^q\; dx-\int_{\om}|\bar{u}(x)|\; dx\right).
        \end{split}
    \end{equation}
In order to analyze the sign of the right hand part of \eqref{eq2:theorem2}, 
we must divide $\om$ into two more sets in addition to 
$\om^*$: $\om_1^*:=\{x\in \om:|\bar{u}(x)|\ge \jump_q\}$ and 
$\om^*_2:=\{x\in\om:\bar{u}(x)=0\}$ and split the inner product and the 
integrals present in \eqref{eq2:theorem2} into these domains. Now, for 
almost all $x\in \om_1^*$ we have by the form of $\zeta$ defined in \eqref{optimality_convex} that
\begin{align*}   
\int_{\om_1^*}(\alpha\bar{u}(x)-\zeta(x))&(u(x)-\bar{u}(x))+\beta\left(|u(x)|^q-|\bar{u}(x)|\right)\; dx\\
&=\beta\int_{\om_1^*}|u(x)|^q-|\bar u(x)|^q - \beta q |\bar{u}(x)|^{q-1}\sign(\bar u(x))\;dx    
\end{align*}
Due to the differentiability of the function $t\mapsto \beta |t|^{q}$ for
any $|t|>\jump_q$, we apply a Taylor expansion around $|\bar u(x)|>\jump_q$ of the 
last term of the relation above to obtain

\begin{align}
\int_{\om_1^*} &\beta |u(x)|^q- \beta |\bar u(x)|^q  
-\beta q |\bar u(x)|^{q-1}\sign(\bar u(x))(u(x)- \bar u(x)) dx\nonumber\\
=& \int_{\om_1^*} 
\frac{\beta}{2}q(q-1)|\bar u(x)|^{q-2} (u(x)- \bar u(x))^2 
+ o(|u(x)- \bar u(x)|^2) dx \nonumber\\
\geq & \int_{\om_1^*} 
\frac{\beta}{2}q(q-1){\jump_q}^{q-2} (u(x)- \bar u(x))^2 dx  
+ o(|u(x)- \bar u(x)|^2) \nonumber \\
= & -q\frac{\alpha}{4}\int_{\om_1^*} (u(x)- \bar u(x))^2 dx
>-q\frac{\alpha}{2}\int_{\om_1^*} (u(x)- \bar u(x))^2 dx. 
\label{eq:om1} 
\end{align}

Now, since $\bar{u}(x)=0$ over $\om_{2}^*$, we also have that
\begin{equation}\label{eq4:theorem2}
\begin{split}   
\int_{\om_2^*}(\alpha\bar{u}(x)&-\zeta(x))(u(x)-\bar{u}(x))+\beta\left(|u(x)|^q-|\bar{u}(x)|^q\right)\; dx\\
&=\int_{\om_2^*}\eta u(x)+\beta |u(x)|^q+\frac{\alpha}{2}|u(x)|^2\; dx-\int_{\om_2^*}\frac{\alpha}{2}|u(x)|^2,
    \end{split}
\end{equation}
where $|\eta|\le \omega_q$, according to the form of $\zeta$ in 
\eqref{optimality_convex}. Define the unidimensional function 
$\varphi(t):=\eta t+\beta|t|^q+\frac{\alpha}{2}|t|^2$ for all $t\in \mathbb{R}$, and
notice that $\beta|t|^q+\frac{\alpha}{2}|t|^2\ge \omega_q |t|$, according to 
Proposition \ref{prop:phi**_quadrature}. Thus $ \varphi(t)\ge \omega_q|t|+\eta t=|t|(\omega_q+\eta\sign(t))\ge 0$,
since $\eta\sign(t)\in [-\omega_q,\omega_q]$. Therefore, 
\[
\eta u(x)+\beta |u(x)|^q+\frac{\alpha}{2}|u(x)|^2\ge 0,
\]
for all $x\in \om_2^*$, and \eqref{eq4:theorem2} is equivalent to
\begin{equation}\label{eq5:theorem2}
\begin{split}   
\int_{\om_2^*}(\alpha\bar{u}(x)-\zeta(x))(u(x)-\bar{u}(x))+&\beta\left(|u(x)|^q-|\bar{u}(x)|^q\right)\; dx\\
&\ge-\int_{\om_2^*}\frac{\alpha}{2}|u(x)|^2\; dx,
    \end{split}
\end{equation}
Recalling \eqref{eq1:theorem2} and combining \eqref{eq:om1} and \eqref{eq4:theorem2} we have that
\begin{align*}
    J(y,u)-J(\bar{y},\bar{u})&>\frac{\alpha}{2}\norm{u-\bar{u}}_{L^2(\om)}^2-q\frac{\alpha}{2}\int_{\om_1^*}(u(x)-\bar{u}(x))^2\; dx -\int_{\om_2^*}\frac{\alpha}{2}|u(x)|^2\\
    &\phantom{>}+\frac{1}{2}\norm{y-\bar{y}}_{L^2(\om)}^2\\    
    &\ge (1-q)\frac{\alpha}{2}\int_{\om_1^*}(u(x)-\bar{u}(x))^2\; dx\ge 0,
\end{align*}
proving that $(\bar{y},\bar{u})$ is optimal for \eqref{plambda}.
\end{proof}

\section{$L^0(\om)$ penalized control problems}

In this section we recall the known results about existence of solutions
and optimalityconditions for problems like \eqref{eq:OCP} when $q=0$. In the 
finite dimensional setting and related to the compressed sensing, Donoho \cite{donoho} it is introduced
a function $\norm{\cdot}_0$ which, for every $\theta\in\ell^0$, $\norm{\theta}_0$ counts the number 
of nonzeros entries of $\theta$. 

K. Ito and K. Kunish \cite{ito-kunisch2014} propose an extension of this regularization to the optimal control
setting. In this work, it is considered the $L^0(\om)$ space endowed with the Eckeland distance \eqref{eq:Eckeland}.
As we discuss in subsection \ref{subsec:l0_space}, the term $d_0(f,0)$ defines the 
pseudonorm $\norm{f}_{L^0}$. To establish existence and possible unicity of solutions for
the control problem, they first study the general problem:
\begin{equation}\label{eq:P0}
\tag{$P_{0}$}
\left\{
\begin{aligned}
\min \;& \int_{\Omega} \big( \ell(x, y(\omega)) + h(u(x)) \big)\; dx \\[0.3em]
\text{s.t. }\;& E y + f(\cdot, y, u) = 0 \quad \text{in } X^*, \\[0.3em]
& u \in U_{ad} = \{ u \in L^2(\Omega) : u(x) \in U \ \text{a.e.} \}.
\end{aligned}
\right.
\end{equation}

where $U$ is a closed convex subset of $\mathbb{R}$ and 
$E \in \mathcal{L}(X, X^*)$ with $X^*$ the dual space of $X$. 
Further, $f \in C^1(\Omega \times \mathbb{R}^2, \mathbb{R})$, 
$\ell : \Omega \times \mathbb{R} \to \mathbb{R}$ is measurable and $C^1$ with respect to the second variable, and 
$h : \mathbb{R} \to \mathbb{R}$ is measurable. For this general problem, they define the Hamiltonian
associated to \eqref{eq:P0}, $\mathcal{H} : \mathbb{R}^4 \to \mathbb{R}$,
 by
\[
\mathcal{H}(x,y,u,p)
= \ell(x,y) + h(u) + p\, f(x,y,u).
\]
The following set ot conditions are needed in order to derive a like--Pontryagin maximum
principle for \eqref{eq:P0}

\begin{enumerate}
\item The substitution operator associated with $f$ is well defined, namely
\[
(y,u) \in X \times U_{ad}
\;\longrightarrow\;
f_y(\cdot,y,u) \in \mathcal{L}(X,X^*).
\]

\item The substitution operator associated with $\ell$ satisfies
\[
\ell_y(\cdot,y) \in L^1(\om)\cap X^*
\qquad \text{for all } y \in X.
\]

\item The adjoint equation
\[
(E + f_y(\cdot,\bar{y},\bar{u}))^* p
+ \ell_y(\cdot,\bar{y}) = 0
\]
is well defined and admits a unique solution $p \in X$.

\item For arbitrary $s \in \om$, needle perturbations of the optimal control
$\bar u$ are defined by
\[
v(x)=
\begin{cases}
u, & \text{if } x \in B(s,\delta)
= \{ x \in \om : |x-s|<\delta \},\\
\bar{u}(x), & \text{otherwise},
\end{cases}
\]
where $u \in U$ is constant and $\delta>0$ is sufficiently small so that
$B(s,\delta)\subset\om$.

\item In addition, the following properties must hold:
\begin{equation}
\label{eq:additional_properties}
\left\{
\begin{aligned}
&\|y(v)-\bar{y}\|_{L^2(\om)}^2
= o\big(\operatorname{meas}(B(s,\delta))\big), \\[0.8em]
&\int_{\om}
\Big(
\ell(x,y(v))
- \ell(x,\bar{y})
- \ell_y(x,\bar{y})\,(y(v)-\bar{y})
\Big)\,dx
= O\big(\|y(v)-\bar{y}\|_{L^2(\om)}^2\big), \\[1em]
&\Big\langle
f(\cdot,y(v),v)
- f(\cdot,\bar{y},v)
- f_y(\cdot,\bar{y},v)\,(y(v)-\bar{y}),
\, p
\Big\rangle_{X^*,X}
= O\big(\|y(v)-\bar{y}\|_{X}^2\big), \\[1em]
&\big(
f_y(\cdot,\bar{y},u)
- f_y(\cdot,\bar{y},\bar{u})
\big)p
\in L^2(\om)
\quad \text{for each } u \in U.
\end{aligned}
\right.
\end{equation}
\end{enumerate}
With all those assumptions, in \cite[Theorem 2.2]{ito-kunisch2014} it is established that under
te supposition $(\bar y,\bar u) \in X \times U_{ad}$ is optimal for problem $(P_{0})$ and if 
$p \in X$ satisfies the adjoint equation
\[
(E + f_y(\cdot,\bar y,\bar u))^* p
+ \ell_y(\cdot,\bar y) = 0,
\]
the following necessary optimality condition holds: for every $u \in U$,
\begin{equation}\label{eq:pontryagin}
\mathcal H(x,\bar y(x),u,p(x))
-
\mathcal H(x,\bar y(x),\bar u(x),p(x))
\ge 0
\quad \text{for a.e. } x \in \om.
\end{equation}

Under the assuption that the measure of the set 
$\{x\in \om: |p(x)|=\sqrt{2\alpha\beta}\}$ is zero, Theorems 2.7 and 2.11 
of \cite{ito-kunisch2014} tell us that \eqref{eq:OCP} with $q=0$
has a unique solution. The proof of this fact follows from the 
like--Pontryagin principle derived before. Moreover, by Remark 2.9 we have that
if the hypothesis over the adjoint state is not impossed, the existence of
solution for \eqref{eq:OCP} with $q=0$ is not guaranteed. In adition, the $\Gamma$--regularization
aproach is suggested in Remark 2.10 as an alternative way to explore the
existence of solutions for \eqref{eq:OCP} with $q=0$.

An ampliation of the results of \cite{ito-kunisch2014} respect to the 
$L^0$ penalized problem, can be found in \cite{casasl0}. In this work,
E. Casas and D. Wachsmuth consider a similar problem like \eqref{eq:OCP} with
$q=0$, but instead of a linear PDE, a semilinear PDE is considered. 

Under suitable conditions about the semilinearity of the PDE, necessary first 
order optimality conditions can be derived \cite[Theorem 3.1]{casasl0}, and 
moreover, a similar result as Corollary \ref{corollary:null_solution}
is established, see \cite[Corollary 3.3]{casasl0}. 

Another novelty in this work is the fact that second necessary and 
sufficient optimality conditions for \eqref{eq:OCP} with $q=0$ are given. Respect 
to the necessary conditions, it is established that if $\bar u$ be locally optimal for the
semilinear problem, it holds
\[
F''(\bar u)(v,v) + \alpha \|v\|_{L^2(\Omega)}^2 \ge 0
\]
for all $v \in C_{\bar u}$, where the critical cone $C_{\bar u}$ is given by
\[
C_{\bar u}
=
\left\{
v \in T_{U_{ad}}(\bar u)
:
\; v(x)=0
\ \text{if } \bar u(x)=0
\ \text{or } \bar\varphi(x)+\alpha \bar u(x) \neq 0
\right\},
\]
and
\[
T_{U_{ad}}(\bar u)
=
\left\{
v \in L^2(\Omega) :
\begin{aligned}
&v(x) \ge 0 && \text{if } \bar u(x) = -\gamma,\\
&v(x) \le 0 && \text{if } \bar u(x) = +\gamma
\end{aligned}
\right\}.
\]
Here $\varphi$ is the adjoint state of the semilinear problem, and $F$ is the 
smooth part of the cost fucntion of \eqref{eq:OCP} that contains only the state $y$.

Finally, in order to derive second-order sufficient optimality conditions 
for the semilinear problem, it is necessary to introduce the follwing cones:

\[
D_{\bar u}^{\tau}
:=
\left\{
v \in T_{U_{ad}}(\bar u) :
\begin{aligned}
&v(x) \ge 0 && \text{if } \bar u(x)=0 \text{ and } \bar\varphi(x) = -\sqrt{2\alpha\beta},\\
&v(x) \le 0 && \text{if } \bar u(x)=0 \text{ and } \bar\varphi(x) = \sqrt{2\alpha\beta},\\
&v(x) = 0 && \text{if } |\bar\varphi(x)| \le \sqrt{2\alpha\beta}-\tau
\text{ or } |\bar\varphi(x)| \ge \alpha\gamma+\tau
\end{aligned}
\right\},
\]

\[
E_{\bar u}^{\tau}
:=
\left\{
v \in T_{U_{ad}}(\bar u) :
F'(\bar u)v + G'(\bar u;v)
\le \tau \|v\|_{L^2(\Omega)}
\right\},
\]

and
\[
C_{\bar u}^{\tau}
:=
D_{\bar u}^{\tau} \cap E_{\bar u}^{\tau}.
\]

Then, since a Pontryagin-type maximum principle, analogous to 
\eqref{eq:pontryagin}, can be established for the semilinear problem, and 
assuming that $\bar u$ satisfies this principle and that there exist 
$\delta > 0$ and $\tau > 0$ such that
\[
F''(\bar u)v^2 + \tilde G(\bar u;v^2)
\ge \delta \|v\|_{L^2(\Omega)}^2
\qquad \forall v \in C_{\bar u}^{\tau}.
\]
then, by \cite[Theorem 4.21]{casasl0}, there exist $\rho > 0$ and 
$\kappa > 0$ such that
\[
J(\bar u) + \kappa \|u-\bar u\|_{L^2(\Omega)}^2
\le J(u)
\]
for all $u \in B_\rho(\bar u)\cap U_{ad}$.
Moreover, $\big( B_\rho(\bar u)\cap U_{ad} \big)\setminus \{\bar u\}$ does not contain any control satisfying the Pontryagin principle for $(P)$. Here 
\[
\tilde G(\bar u; v^2)
:=
\alpha
\int_{\{x \in \Omega:\, |\bar u(x)| \ge \sqrt{2\beta/\alpha},\;
\operatorname{sign}(v(x))=\operatorname{sign}(\bar u(x))\}}
v^2 \, dx.
\]
Other conditions are deduced under some estructural proerties that
generalize the hypothesis of the nullity of the measure of the set
$\{x\in\om: |\varphi(x)| = \sqrt{2\beta/\alpha}\}$. However, the authors
explain that the main result of their paper is Theorem 4.21. 


 
	




